---
title: "AR1 analyses of Gilleen data"
author: "Gary Napier"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

<!-- arguments -->

```{r echo = FALSE, cache=F}
#
Subjects <- 1
Plot_subj <- FALSE

Analyses_nos <- c(19, 21)

Do_stats = TRUE
Do_plots = TRUE

```

<!-- Custom functions, load data & clean -->

```{r echo = FALSE,  warning=FALSE, message=FALSE, cache=FALSE}

tryCatch({
setwd("U:\\Gilleen_data")
}, error=function(e){
setwd("~/Dropbox/Gilleen_Analysis/For Gary")
})

# Source packages and custom functions
source("https://raw.githubusercontent.com/GaryNapier/Packages_functions/master/PACKAGES.R")
library(htmlTable) # FFS!

#---------------------------------------
# Load in data & clean
#---------------------------------------

# Read in data from CSV and Matlab files
# Gillen CSV file is for getting the groups (control/patient/normal control)
if (!exists("Gilleen") | !exists("Gilleen_analyses")){
  Gilleen_PDG_data <<- readMat("Gilleen_PDG_data_flip.mat")
  Gilleen_beads_data <<- readMat("Gilleen_Beads_data_flip.mat")
  Gilleen_analyses_results <<- readMat("Gilleen_analysis_results.mat")
}

# # Get groups and clean data
# Group <- Gilleen$cond
# Group <- Group[complete.cases(Group)]
# levels(Group)[levels(Group) == "normal control"] <- "Control"
# levels(Group)[levels(Group) == "deluded"] <- "Patient"
# Group <- factor(Group, levels = c("Control", "Patient"))
# Group_names <- as.character(unique(Group))

#---------------------------------------
# Misc setup
#---------------------------------------

# Groups
Ctrl <- 1:112
Pat <- 113:168
Group <- factor(c(rep("Control", max(Ctrl)), rep("Patient", max(Pat)-min(Pat)+1)), 
                 levels = c("Control", "Patient"))
Group_names <- as.character(unique(Group))

# For tables
Blue <- "#F1F0FA"
Table_options <- list(align=c("c","|"), align.header =c("c","|"), col.columns = c("none",Blue) )

# Save names of priors
Priors <- c("NuPrimeMu", "NuPrimeSa", "KappaMu", "KappaSa", "OmegaMu",
            "OmegaSa", "ThetaMu", "ThetaSa", "mMu", "mSa", "PhiMu", "PhiSa", "Sig2Mu", "Sig2Sa")

Priors_names <- c("NuPrimeMu", "NuPrimeSa", "KappaMu", "KappaSa", "Om2Mu",
            "Om2Sa", "Om3Mu", "Om3Sa",  "ThetaMu", "ThetaSa", "m2Mu", "m2Sa",
            "m3Mu", "m3Sa", "Phi2Mu", "Phi2Sa", "Phi3Mu", "Phi3Sa", "Sig2Mu", "Sig2Sa")

# Priors_names <- c("NuPrimeMu", "NuPrimeSa", "KappaMu", "KappaSa", "Om2Mu","Om2Sa", "m2Mu", "m2Sa",
#              "Phi2Mu", "Phi2Sa", "Sig2Mu", "Sig2Sa")
  
# Misc
options(digits = 4)
N_groups <- length(Group_names)
# Parameter_names <- c("Om2", "Om3", "log(Nu)", "M2", "M3", "Phi2", "Phi3")
Parameter_names <- c("Sa2", "Om2", "log(Nu)", "M2", "Phi2")
N_parameters <- length(Parameter_names)
N_subjects <- length(Gilleen_analyses_results[[1]][[1]][[1]][[1]])
N_analyses <- length(Analyses_nos)

Datasets <- unlist(lapply(seq(length(Gilleen_analyses_results[[1]])),
              function(i) {Gilleen_analyses_results[[1]][[i]][[1]][, , 1][["Dataset.used"]]}))

Datasets <- gsub("data", "", Datasets)

Datasets <- Datasets[Analyses_nos]

Mw_names <-  c("Z", "p", "r")

# Get model names/numbers
Model_names <- sprintf("A%g_%s", Analyses_nos, Datasets)  

#----------------------------------------------------------------
# Get & display parameter priors used for each selected analysis
#----------------------------------------------------------------

# Create data frames of priors for selected analyses 
# Separate data frames for original and AR1 models
Priors_df <- data.frame()
Priors_df_AR1 <- list()
for (i in seq(Analyses_nos)){
   Priors_df_AR1[[i]] <- Gilleen_analyses_results[[1]][[Analyses_nos[i]]][[1]][,,1][c(Priors)]
}

# AR1 priors - horrible data-cleaning excercise!
Priors_df_AR1 <- Priors_df_AR1[!sapply(Priors_df_AR1, is.null)]
Priors_df_AR1 <- lapply(Priors_df_AR1, function(x) x[!sapply(x, is.null)])
Priors_df_AR1 <- lapply(Priors_df_AR1, function(x) lapply(x, function(x){
  paste(as.character(signif(x, digits = 3)), collapse = ", ")
}))
Priors_df_AR1 <- plyr::ldply(lapply(Priors_df_AR1, data.frame), data.frame)
rownames(Priors_df_AR1) <- Model_names

# # Add analyses numbers as row names for each dataframe
# for (i in seq(Analyses_nos)){
#   if (Analyses_nos[i] <= 10){
#    rownames(Priors_df)[i] <- Model_names[i]
#   }else if (Analyses_nos[i] > 10 & length(Priors_df_AR1) > 1){
#    rownames(Priors_df_AR1)[i - nrow(Priors_df)] <- Model_names[i]
#   }
# }

# Tests for R markdown evaluation:
# Priors_df_test <- nrow(Priors_df) > 1
# Priors_df_AR1_test <- nrow(Priors_df_AR1) > 1
  
```
### **Parameter priors**
#### AR1 model analyses:
`r  do.call("htmlTable", c(list(Priors_df_AR1), Table_options))`
**-------------------------------------------------------------------------------------------**

<!-- GET POSTERIORS AND STATS TO PASS TO PLOTS/ DISPLAYS -->

```{r echo=FALSE,  warning=FALSE, message=FALSE, cache=F}

# Get posteriors from selected analyses - for overall stats
Sa2_vector <- vector("list", length(Gilleen_analyses_results[[1]]))
Om2_vector <- vector("list", length(Gilleen_analyses_results[[1]]))
Om3_vector <- vector("list", length(Gilleen_analyses_results[[1]]))
Nu_vector <- vector("list", length(Gilleen_analyses_results[[1]]))
M2_vector  <- vector("list", length(Gilleen_analyses_results[[1]]))
M3_vector  <- vector("list", length(Gilleen_analyses_results[[1]]))
Phi2_vector<- vector("list", length(Gilleen_analyses_results[[1]]))
Phi3_vector<- vector("list", length(Gilleen_analyses_results[[1]]))
for (j in seq_along(Analyses_nos)){
  for (i in 1:N_subjects){
Sa2_vector[[Analyses_nos[j]]][i] <- Gilleen_analyses_results[[1]][[Analyses_nos[j]]][[1]][[1]][[i]][[1]][9][[1]][2][[1]][,2]
Om2_vector[[Analyses_nos[j]]][i] <- Gilleen_analyses_results[[1]][[Analyses_nos[j]]][[1]][[1]][[i]][[1]][9][[1]][[6]][2]
Om3_vector[[Analyses_nos[j]]][i] <- Gilleen_analyses_results[[1]][[Analyses_nos[j]]][[1]][[1]][[i]][[1]][9][[1]][[6]][3]
Nu_vector[[Analyses_nos[j]]][i] <- Gilleen_analyses_results[[1]][[Analyses_nos[j]]][[1]][[1]][[i]][[1]][[10]][[1]][1]
M2_vector[[Analyses_nos[j]]][i] <- Gilleen_analyses_results[[1]][[Analyses_nos[j]]][[1]][[1]][[i]][[1]][9][[1]][[4]][2]
M3_vector[[Analyses_nos[j]]][i] <- Gilleen_analyses_results[[1]][[Analyses_nos[j]]][[1]][[1]][[i]][[1]][9][[1]][[4]][3]
Phi2_vector[[Analyses_nos[j]]][i] <- Gilleen_analyses_results[[1]][[Analyses_nos[j]]][[1]][[1]][[i]][[1]][9][[1]][[3]][2]
Phi3_vector[[Analyses_nos[j]]][i] <- Gilleen_analyses_results[[1]][[Analyses_nos[j]]][[1]][[1]][[i]][[1]][9][[1]][[3]][3]
  }#for (i in 1:N_subjects)
}#for (j in Analyses_nos)
 
# Clear NULL values from lists
Sa2_vector <- Sa2_vector[vapply(Sa2_vector, Negate(is.null), NA)]
Om2_vector <- Om2_vector[vapply(Om2_vector, Negate(is.null), NA)]
Om3_vector <- Om3_vector[vapply(Om3_vector, Negate(is.null), NA)]
Nu_vector <- Nu_vector[vapply(Nu_vector, Negate(is.null), NA)]
M2_vector  <- M2_vector[vapply(M2_vector, Negate(is.null), NA)]
M3_vector  <- M3_vector[vapply(M3_vector, Negate(is.null), NA)]
Phi2_vector<- Phi2_vector[vapply(Phi2_vector, Negate(is.null), NA)]
Phi3_vector<- Phi3_vector[vapply(Phi3_vector, Negate(is.null), NA)]

# Transform Nu
Nu_vector <- lapply(Nu_vector, log)

# Make list of data frames for ANOVA (t-test) analyses
Sa2_vector <- lapply(Sa2_vector, function(Sa2_vector) cbind.data.frame(Group, Sa2_vector)) 
Om2_vector <- lapply(Om2_vector, function(Om2_vector) cbind.data.frame(Group, Om2_vector))
Om3_vector <- lapply(Om3_vector, function(Om3_vector) cbind.data.frame(Group, Om3_vector))
Nu_vector <- lapply(Nu_vector, function(Nu_vector) cbind.data.frame(Group, Nu_vector))
M2_vector  <- lapply(M2_vector, function(M2_vector) cbind.data.frame(Group, M2_vector))
M3_vector  <- lapply(M3_vector, function(M3_vector) cbind.data.frame(Group, M3_vector))
Phi2_vector<- lapply(Phi2_vector, function(Phi2_vector) cbind.data.frame(Group, Phi2_vector))
Phi3_vector<- lapply(Phi3_vector, function(Phi3_vector) cbind.data.frame(Group, Phi3_vector))
  
# Measure fit for whole analyses selected

# Get responses (i.e. data), bead seq & HGF predictions
Responses <- vector("list", length(Gilleen_analyses_results[[1]]))
Beads <- vector("list", length(Gilleen_analyses_results[[1]]))
Predictions <- vector("list", length(Gilleen_analyses_results[[1]]))
Mu2_0 <- vector("list", length(Gilleen_analyses_results[[1]]))
Learning_rate <- vector("list", length(Gilleen_analyses_results[[1]]))
for (j in seq_along(Analyses_nos)){
  for (i in 1:N_subjects){
# r.y:
Responses[[Analyses_nos[j]]][[i]] <- Gilleen_analyses_results[[1]][[Analyses_nos[j]]][[1]][[1]][[i]][[1]][[1]]
# r.u:
Beads[[Analyses_nos[j]]][[i]] <- Gilleen_analyses_results[[1]][[Analyses_nos[j]]][[1]][[1]][[i]][[1]][[2]]
  # r.traj.mu:
  Predictions[[Analyses_nos[j]]][[i]] <- Tapas_sgm(Gilleen_analyses_results[[1]][[Analyses_nos[j]]][[1]][[1]][[i]][[1]][[11]][[1]][,2], 1) 
  # r.p_prc.mu2_0; the '0th' prediction (prior):
  Mu2_0[[Analyses_nos[j]]][[i]] <- Tapas_sgm(Gilleen_analyses_results[[1]][[Analyses_nos[j]]][[1]][[1]][[i]][[1]][[9]][[1]][2], 1)
  # r.traj.wt; Learning rate
  Learning_rate[[Analyses_nos[j]]][[i]] <- Gilleen_analyses_results[[1]][[Analyses_nos[j]]][[1]][[1]][[i]][[1]][[11]][[11]][,1]
  }#(i in 1:N_subjects)
}#(j in 1:length(Analyses_nos))

# Remove NULLS. Not sure why each one is different...
Responses <- Responses[vapply(Responses, Negate(is.null), NA)]
Beads <- Beads[vapply(Beads, Negate(is.null), NA)]
Predictions <- Predictions[vapply(Predictions, Negate(is.null), NA)]
Mu2_0 <- Filter(Negate(is.null), Mu2_0)
Learning_rate <- Learning_rate[vapply(Learning_rate, Negate(is.null), NA)]
# DONE

# Useful!
N_beads <- lapply(Beads, function(x) unlist(unique(lapply(x, length))))
N_predictions <- lapply(Predictions, function(x) unlist(unique(lapply(x, length))))
N_responses <- lapply(Responses, function(x) unlist(unique(lapply(x, length))))

# Pre-allocate for for-loops
Opp_bead_indeces <- vector("list", length(Beads)) 
Opp_bead_indeces <- lapply(Opp_bead_indeces, function(x){
  vector("list", N_subjects)
})

# Loops for getting true/false for 'bead of opposite colour' from bead seqs
for (k in 1:length(Beads)){
  for (j in 1:length(Beads[[k]])){
    for(i in 2:length(Beads[[k]][[j]])){
      Opp_bead_indeces[[k]][[j]][i] <- !(Beads[[k]][[j]][i]-Beads[[k]][[j]][i-1] == 0)
    }
  }
}
# Find indeces
Opp_bead_indeces <- lapply(Opp_bead_indeces, function(x){
  lapply(x, function(y) which(y == TRUE))
})
Fit_BOOC_whole_model <- vector("list", length(Analyses_nos))

for (i in 1:length(Opp_bead_indeces)){
  for (j in 1:length(Opp_bead_indeces[[i]])){
    
    Fit_BOOC_whole_model[[i]][j] <- 
      signif(sum((Responses[[i]][[j]][Opp_bead_indeces[[i]][[j]]] 
                  - Predictions[[i]][[j]][Opp_bead_indeces[[i]][[j]]])^2), digits = 2)
  }
}
  
# Make a copy to pass to 'individual subjects' section - allows simple 
# subsetting of BOOC fit by subjects selected
Fit_BOOC_whole_model_copy <- Fit_BOOC_whole_model
# Weight Fit_BOOC_whole_model_copy by length of trials (number of beads) divided by 10 
Fit_BOOC_subject <- lapply(seq_along(Fit_BOOC_whole_model_copy), function(i){
  (Fit_BOOC_whole_model_copy[[i]]/(N_beads[[i]]/10))
})

# Take the mean of the fits and adjust by length of bead seq (N_beads) for each analysis
Fit_BOOC_whole_model <- lapply_mod(Fit_BOOC_whole_model,
                                   function(i) mean(Fit_BOOC_whole_model[[i]])/N_beads[[i]])

# For predictions, need to concatenate Mu2_0 prior at the start of each Prediction vector
for (j in seq(Predictions))
  for (i in seq(Predictions[[j]])){
    Predictions[[j]][[i]] <- append(Predictions[[j]][[i]], Mu2_0[[j]][i], 0)
  }

```

### **Means, SDs, t-test & non-parametric summaries**

#### Mean/SD table

```{r echo = FALSE, results = 'asis', warning=FALSE, message=FALSE, cache=F}
    
    Col_names <- c("Mean", "SD")
    # SA2
    Sa2_mean_sd <- do.call("rbind", lapply( lapply( Sa2_vector, function(x) {
     data.frame(rbind(
          c(mean(x$Sa2_vector[Ctrl]), sd(x$Sa2_vector[Ctrl])), 
          c(mean(x$Sa2_vector[Pat]), sd(x$Sa2_vector[Pat]))
          ) ) 
    }) ,setNames, Col_names ))

    # OMEGA2
    # Mean / sd groups
    Om2_mean_sd <- do.call("rbind", lapply( lapply( Om2_vector, function(x) {
     data.frame(rbind(
          c(mean(x$Om2_vector[Ctrl]), sd(x$Om2_vector[Ctrl])), 
          c(mean(x$Om2_vector[Pat]), sd(x$Om2_vector[Pat]))
          ) ) 
    }) ,setNames, Col_names ))
    
    # OMEGA3
    # Om3_mean_sd <- do.call("rbind", lapply( lapply( Om3_vector, function(x) {
    #  data.frame(rbind(
    #       c(mean(x$Om3_vector[Ctrl]), sd(x$Om3_vector[Ctrl])), 
    #       c(mean(x$Om3_vector[Pat]), sd(x$Om3_vector[Pat]))
    #       ) ) 
    # }) ,setNames, Col_names ))
  
    # NU
    # Mean/sd groups
    Nu_mean_sd <- do.call("rbind", lapply( lapply( Nu_vector, function(x) {
     data.frame(rbind(
          c(mean(x$Nu_vector[Ctrl]), sd(x$Nu_vector[Ctrl])), 
          c(mean(x$Nu_vector[Pat]), sd(x$Nu_vector[Pat]))
          ) ) 
    }) ,setNames, Col_names ))
      
    # M2
    # Mean/sd groups
    M2_mean_sd <-   do.call("rbind", lapply( lapply( M2_vector, function(x) {
     data.frame(rbind(
          c(mean(x$M2_vector[Ctrl]), sd(x$M2_vector[Ctrl])), 
          c(mean(x$M2_vector[Pat]), sd(x$M2_vector[Pat]))
          ) ) 
    }) ,setNames, Col_names ))
    
    # M3
    # M3_mean_sd <-   do.call("rbind", lapply( lapply( M3_vector, function(x) {
    #  data.frame(rbind(
    #       c(mean(x$M3_vector[Ctrl]), sd(x$M3_vector[Ctrl])), 
    #       c(mean(x$M3_vector[Pat]), sd(x$M3_vector[Pat]))
    #       ) ) 
    # }) ,setNames, Col_names ))
    # 
    # PHI2
    # Mean / sd groups
    Phi2_mean_sd <-   do.call("rbind", lapply( lapply( Phi2_vector, function(x) {
     data.frame(rbind(
          c(mean(x$Phi2_vector[Ctrl]), sd(x$Phi2_vector[Ctrl])), 
          c(mean(x$Phi2_vector[Pat]), sd(x$Phi2_vector[Pat]))
          ) ) 
    }) ,setNames, Col_names ))
      
    # PHI3
    # Mean / sd groups
    # Phi3_mean_sd <- do.call("rbind", lapply( lapply( Phi3_vector, function(x) {
    #  data.frame(rbind(
    #       c(mean(x$Phi3_vector[Ctrl]), sd(x$Phi3_vector[Ctrl])),
    #       c(mean(x$Phi3_vector[Pat]), sd(x$Phi3_vector[Pat]))
    #       ) )
    # }) ,setNames, Col_names ))
    
    # Bring all means, SDs together
    # Mean_sd <- cbind(Om2_mean_sd, Om3_mean_sd, Nu_mean_sd, M2_mean_sd, M3_mean_sd, Phi2_mean_sd, Phi3_mean_sd)
      # Mean_sd <- cbind(Sa2_mean_sd, Om2_mean_sd, Om3_mean_sd, Nu_mean_sd, M2_mean_sd, M3_mean_sd, Phi2_mean_sd, Phi3_mean_sd)
  Mean_sd <- cbind(Sa2_mean_sd, Om2_mean_sd, Nu_mean_sd, M2_mean_sd, Phi2_mean_sd)
  
  htmlTable(txtRound(Mean_sd, digits = 2),
            rnames=rep(Group_names, N_analyses), 
            rgroup = Model_names, 
            n.rgroup=rep(N_groups, N_analyses), 
            cgroup = Parameter_names, 
            n.cgroup= rep(2, N_parameters), 
            align = c("c", "|"), align.header=c("c", "|"), col.columns=c("none", "none", Blue, Blue))
  


```

#### Summary of t-tests

<!--  CREATE & DISPLAY parametric models - t-tests -->
```{r echo=FALSE, cache=F}

# Create t-tests:
# Sa2
T_Sa2_tests <- lapply(Sa2_vector, function(x)
      tryCatch({
      t.test(x$Sa2_vector ~ x$Group) # Try this first
      }, error = function(e) {
      NA # error-handler-code (Do this if error)
      }) # tryCatch
  ) # lapply
T_Sa2 <- do.call("rbind", T_Sa2_tests)
T_Sa2 <- data.frame(T_Sa2[,c("statistic", "parameter", "p.value")])
T_Sa2 <- cbind(T_Sa2,
               Effect = unlist(lapply(Sa2_vector,
                function(x) cohensD(Sa2_vector ~ Group, data = x))))

# Om2
T_om2_tests <- lapply(Om2_vector, function(x)
      tryCatch({
      t.test(x$Om2_vector ~ x$Group) # Try this first
      }, error = function(e) {
      NA # error-handler-code (Do this if error)
      }) # tryCatch
  ) # lapply
T_om2 <- do.call("rbind", T_om2_tests)
T_om2 <- data.frame(T_om2[,c("statistic", "parameter", "p.value")])
T_om2 <- cbind(T_om2, 
               Effect = unlist(lapply(Om2_vector,
                function(x) cohensD(Om2_vector ~ Group, data = x))))

# om3
# T_om3 <- lapply(Om3_vector, function(x)
#       tryCatch({
#       t.test(x$Om3_vector ~ x$Group) # Try this first
#       }, error = function(e) {
#       NA # error-handler-code (Do this if error)
#       }) # tryCatch
#   ) # lapply
# T_om3 <- do.call("rbind", T_om3)
# T_om3 <- data.frame(T_om3[,c("statistic", "parameter", "p.value")])
# T_om3 <- cbind(T_om3, 
#                Effect = unlist(lapply(Om3_vector,
#                 function(x) cohensD(Om3_vector ~ Group, data = x))))

# Nu
T_Nu <- lapply(Nu_vector, function(x)
      tryCatch({
      t.test(x$Nu_vector ~ x$Group) # Try this first
      }, error = function(e) {
      NA # error-handler-code (Do this if error)
      }) # tryCatch
  ) # lapply
T_Nu <- do.call("rbind", T_Nu)
T_Nu <- data.frame(T_Nu[,c("statistic", "parameter", "p.value")])
T_Nu <- cbind(T_Nu, 
              Effect = unlist(lapply(Nu_vector,
                function(x) cohensD(Nu_vector ~ Group, data = x))))

# M2
T_M2 <- lapply(M2_vector, function(x)
      tryCatch({
      t.test(x$M2_vector ~ x$Group) # Try this first
      }, error = function(e) {
      NA # error-handler-code (Do this if error)
      }) # tryCatch
  ) # lapply
T_M2 <- do.call("rbind", T_M2)
T_M2 <- data.frame(T_M2[,c("statistic", "parameter", "p.value")])
T_M2 <- cbind(T_M2, 
              Effect = unlist(lapply(M2_vector,
                function(x) cohensD(M2_vector ~ Group, data = x))))

# M3
# T_M3 <- lapply(M3_vector, function(x)
#       tryCatch({
#       t.test(x$M3_vector ~ x$Group) # Try this first
#       }, error = function(e) {
#       NA # error-handler-code (Do this if error)
#       }) # tryCatch
# ) # lapply
# T_M3 <- do.call("rbind", T_M3)
# T_M3 <- data.frame(T_M3[,c("statistic", "parameter", "p.value")])
# T_M3 <- cbind(T_M3, 
#               Effect = unlist(lapply(M3_vector,
#                function(x) cohensD(M3_vector ~ Group, data = x))))

# Phi2
T_Phi2 <- lapply(Phi2_vector, function(x)
      tryCatch({
      t.test(x$Phi2_vector ~ x$Group) # Try this first
      }, error = function(e) {
      NA # error-handler-code (Do this if error)
      }) # tryCatch
  ) # lapply
T_Phi2 <- do.call("rbind", T_Phi2)
T_Phi2 <- data.frame(T_Phi2[,c("statistic", "parameter", "p.value")])
T_Phi2 <- cbind(T_Phi2, 
                Effect = unlist(lapply(Phi2_vector,
                 function(x) cohensD(Phi2_vector ~ Group, data = x))))

# Phi3
T_Phi3 <- lapply(Phi3_vector, function(x)
      tryCatch({
      t.test(x$Phi3_vector ~ x$Group) # Try this first
      }, error = function(e) {
      NA # error-handler-code (Do this if error)
      }) # tryCatch
  ) # lapply
T_Phi3 <- do.call("rbind", T_Phi3)
T_Phi3 <- data.frame(T_Phi3[,c("statistic", "parameter", "p.value")])
T_Phi3 <- cbind(T_Phi3, 
                Effect = unlist(lapply(Phi3_vector,
                 function(x) cohensD(Phi3_vector ~ Group, data = x))))


# Labels <- factor(c(rep("Omega2", 1), rep("Omega3", 1),  rep("Nu", 1), rep("M2", 1), 
#                    rep("M3", 1), rep("Phi2", 1), rep("Phi3", 1)), 
#                  levels = c("Omega2", "Omega3", "Nu", "M2", "M3", "Phi2", "Phi3")) 
# Labels <- factor(c(rep("Sa2", 1), rep("Omega2", 1), rep("Omega3", 1),  rep("Nu", 1), rep("M2", 1), rep("M3", 1), rep("Phi2", 1), rep("Phi3", 1)), 
#                  levels = c("Sa2", "Omega2", "Omega3", "Nu", "M2", "M3", "Phi2", "Phi3")) 

Labels <- factor(c(rep("Sa2", 1), rep("Omega2", 1), rep("Nu", 1), rep("M2", 1), rep("Phi2", 1), 
                 levels = c("Sa2", "Omega2", "Nu", "M2", "Phi2"))) 

# Data frame of t-tests
# T_tests_table <- cbind(T_om2, T_om3, T_Nu, T_M2, T_M3, T_Phi2, T_Phi3)
T_tests_table <- cbind(T_Sa2, T_om2, T_Nu, T_M2, T_Phi2)

names(T_tests_table) <- rep(c("t", "df", "p", "d"), N_parameters)

T_tests_table <- sapply(T_tests_table, unlist)

# T_tests_table <- signif(T_tests_table, digits = 2)

htmlTable(txtRound(T_tests_table, digits = 2),
          rnames=Model_names, 
          cgroup = Parameter_names, 
          n.cgroup= rep(4, N_parameters), 
          align = c("c", "|"), align.header=c("c", "|"),
          col.columns=c(rep("none", 4), rep(Blue, 4)), 
          caption = "Welch t-test results, control vs patient")


```

### **Test of t-test assumptions**
##### Shapiro-Wilk test of normality 
##### [<0.05 = NOT normal]

```{r echo = FALSE, cache=F, htmlTable, results = 'asis'}

  # Sa2
  Norm_sa2 <- do.call("rbind", lapply(Sa2_vector, function(x) sapply(split(x$Sa2_vector, Group), Shapiro_NA)))

  # Om2
  Norm_omega2 <- do.call("rbind", lapply(Om2_vector, function(x) sapply(split(x$Om2_vector, Group), Shapiro_NA)))

  # # Om_3
  # Norm_omega3 <- do.call("rbind", lapply(Om3_vector, function(x) sapply(split(x$Om3_vector, Group), Shapiro_NA)))

  # Nu
  Norm_nu <- do.call("rbind", lapply(Nu_vector, function(x) sapply(split(x$Nu_vector, Group), Shapiro_NA)))

  # M2
  Norm_M2 <- do.call("rbind", lapply(M2_vector, function(x) sapply(split(x$M2_vector, Group), Shapiro_NA)))
  
  # # Aov_mod_M3
  # Norm_M3 <- do.call("rbind", lapply(M3_vector, function(x) sapply(split(x$M3_vector, Group), Shapiro_NA)))

  # Phi2
  Norm_phi2 <- do.call("rbind", lapply(Phi2_vector, function(x) sapply(split(x$Phi2_vector, Group), Shapiro_NA)))
  
  # # Phi3
  # Norm_phi3 <- do.call("rbind", lapply(Phi3_vector, function(x) sapply(split(x$Phi3_vector, Group), Shapiro_NA)))

 # Norm_table <- cbind(Norm_omega2, Norm_omega3, Norm_nu, Norm_M2, Norm_M3, Norm_phi2, Norm_phi3)
# Norm_table <- cbind(Norm_sa2, Norm_omega2, Norm_omega3, Norm_nu, Norm_M2, Norm_M3, Norm_phi2, Norm_phi3) 
  
  Norm_table <- cbind(Norm_sa2, Norm_omega2, Norm_nu, Norm_M2, Norm_phi2) 
 
  
 htmlTable(txtRound(Norm_table, digits = 2), 
           rnames=Model_names, 
           cgroup = Parameter_names, 
           n.cgroup = rep(2, N_parameters), 
           align = c("c", "|"), align.header=c("c", "|"),
          col.columns=c(rep("none", 2), rep(Blue, 2)),
          caption = "Tests of normality in posteriors, control and patient (< 0.05 = NOT normal)")


```

**-------------------------------------------------------------------------------------------**

#### Non-parametric tests - Mann-whitney U

```{r echo = FALSE, results = 'asis', warning=FALSE, message=FALSE, cache=F}

  # Sa2 mw
   Sa2_mw <- lapply(Sa2_vector, function(x) wilcox_test(x$Sa2_vector ~ x$Group))
   Sa2_effects <- do.call("rbind", lapply(Sa2_mw, function(x) {Mw_effect(statistic(x), N_subjects)}) )
   Sa2_mw <- do.call("rbind", lapply(Sa2_mw, function(x){c(statistic(x),pvalue(x))}) )
   Sa2_mw <- setNames(data.frame(cbind(Sa2_mw, Sa2_effects)), Mw_names)
   
  # Om2 mw
   Om2_mw <- lapply(Om2_vector, function(x) wilcox_test(x$Om2_vector ~ x$Group))
   Om2_effects <- do.call("rbind", lapply(Om2_mw, function(x) {Mw_effect(statistic(x), N_subjects)}) )
   Om2_mw <- do.call("rbind", lapply(Om2_mw, function(x){c(statistic(x),pvalue(x))}) )
   Om2_mw <- setNames(data.frame(cbind(Om2_mw, Om2_effects)), Mw_names)
    
  # Om3 mw
   # Om3_mw <- lapply(Om3_vector, function(x) wilcox_test(x$Om3_vector ~ x$Group))
   # Om3_effects <- do.call("rbind", lapply(Om3_mw, function(x) {Mw_effect(statistic(x), N_subjects)}) )
   # Om3_mw <- do.call("rbind", lapply(Om3_mw, function(x){c(statistic(x),pvalue(x))}) )
   # Om3_mw <- setNames(data.frame(cbind(Om3_mw, Om3_effects)), Mw_names)
   
  # Nu mw
   Nu_mw <- lapply(Nu_vector, function(x) wilcox_test(x$Nu_vector ~ x$Group))
   Nu_effects <- do.call("rbind", lapply(Nu_mw, function(x) {Mw_effect(statistic(x), N_subjects)}) )
   Nu_mw <- do.call("rbind", lapply(Nu_mw, function(x){c(statistic(x),pvalue(x))}) )
   Nu_mw <- setNames(data.frame(cbind(Nu_mw, Nu_effects)), Mw_names)
   
   # M2 mw
   M2_mw <- lapply(M2_vector, function(x) wilcox_test(x$M2_vector ~ x$Group))
   M2_effects <- do.call("rbind", lapply(M2_mw, function(x) {Mw_effect(statistic(x), N_subjects)}) )
   M2_mw <- do.call("rbind", lapply(M2_mw, function(x){c(statistic(x),pvalue(x))}) )
   M2_mw <- setNames(data.frame(cbind(M2_mw, M2_effects)), Mw_names)
   
   # # M3 mw
   # M3_mw <- lapply(M3_vector, function(x) wilcox_test(x$M3_vector ~ x$Group))
   # M3_effects <- do.call("rbind", lapply(M3_mw, function(x) {Mw_effect(statistic(x), N_subjects)}) )
   # M3_mw <- do.call("rbind", lapply(M3_mw, function(x){c(statistic(x),pvalue(x))}) )
   # M3_mw <- setNames(data.frame(cbind(M3_mw, M3_effects)), Mw_names)
   
   # Phi2 mw
   Phi2_mw <- lapply(Phi2_vector, function(x) wilcox_test(x$Phi2_vector ~ x$Group))
   Phi2_effects <- do.call("rbind", lapply(Phi2_mw, function(x) {Mw_effect(statistic(x), N_subjects)}) )
   Phi2_mw <- do.call("rbind", lapply(Phi2_mw, function(x){c(statistic(x),pvalue(x))}) )
   Phi2_mw <- setNames(data.frame(cbind(Phi2_mw, Phi2_effects)), Mw_names)
   
   # # Phi3 mw
   # Phi3_mw <- lapply(Phi3_vector, function(x) wilcox_test(x$Phi3_vector ~ x$Group))
   # Phi3_effects <- do.call("rbind", lapply(Phi3_mw, function(x) {Mw_effect(statistic(x), N_subjects)}) )
   # Phi3_mw <- do.call("rbind", lapply(Phi3_mw, function(x){c(statistic(x),pvalue(x))}) )
   # Phi3_mw <- setNames(data.frame(cbind(Phi3_mw, Phi3_effects)), Mw_names)
   # 
 # MW_tables <- cbind(Om2_mw, Om3_mw, Nu_mw, M2_mw, M3_mw, Phi2_mw, Phi3_mw)    
 MW_tables <- cbind(Sa2_mw, Om2_mw, Nu_mw, M2_mw, Phi2_mw)
 
 htmlTable(txtRound(MW_tables, digits = 2),
           rnames=Model_names,
           cgroup = Parameter_names, 
           n.cgroup = rep(3, N_parameters),
            align = c("c", "|"), align.header=c("c", "|"),
          col.columns=c(rep("none", 3), rep(Blue, 3)),
          caption = "Mann-whitney U tests")

 
   
```

**-------------------------------------------------------------------------------------------**

### **Fit - beads of opposite colour (BOOC) for selected analyses**

```{r echo = FALSE, results = 'asis', warning=FALSE, message=FALSE, cache=F}

  if (Do_stats == TRUE){ 
#     message("FIT (BOOC)")
#     Dummy_var <- sapply(seq_along(Fit_BOOC_whole_model), function(i) 
#       c(message(sprintf("Fit BOOC for whole analysis %d:", Analyses_nos[i])),
#         print(Fit_BOOC_whole_model[[i]])))
    
   BOOC_data <- data.frame("Analysis_no."=Model_names, 
                           "Fit_BOOC"=signif(unlist(Fit_BOOC_whole_model), digits=3))
   do.call("htmlTable", c(list(BOOC_data), Table_options))
  } # if (Do_stats == TRUE)
 
```
  
**-------------------------------------------------------------------------------------------**

**-------------------------------------------------------------------------------------------**

```{r echo = FALSE, results = 'asis', warning=FALSE, message=FALSE, cache=F}
#---------------------------------------------------------------
# For selected subjects - to pass to subject trajectory plots
#---------------------------------------------------------------

# DONE
# Subset Beads, Responses & Predictions by selected analyses and subjects
Beads_selected <- lapply(Beads, function(x) lapply(x[Subjects], function(x) data.frame(Beads=x)))
Responses_selected <- lapply(Responses, function(x) lapply(x[Subjects], function(x) data.frame(Responses=x)))
Predictions_selected <- lapply(Predictions, function(x) lapply(x[Subjects], function(x) data.frame(Predictions=x)))
Learning_rate_selected <- lapply(Learning_rate, function(x) lapply(x[Subjects], function(x) data.frame(LR=x)))

# x-axes must be from 0 to length of Predictions (for each analysis) in order 
# to align with the responses
x_axes <- vector("list", length(Predictions_selected))
x_axes <- lapply(seq_along(x_axes),
                 function(i) 
                   data.frame(Index = 0:(length("[["(Predictions_selected[[i]][[1]], 1))-1)))
```

### **Plots**

`r if(Plot_subj)'##### Selected subject(s) response trajectory'`

```{r echo = FALSE, results = 'asis', warning=FALSE, message=FALSE, cache=F}
        
# ------------------------------------------------------
# Plot selected subject(s) response trajectory
# ------------------------------------------------------
# Set the default theme
theme_set(theme_grey())

if (Plot_subj == TRUE){
        
for (i in seq_along(Analyses_nos)){
  for (j in seq_along(Subjects)){
      
    # tryCatch({x11()}, error = function(e) {quartz()}, warning = function(w){quartz()}) # New window
      print(ggplot()+
              geom_line(data=Predictions_selected[[i]][[j]],
                        aes(x=x_axes[[i]]$Index, y=Predictions, colour="Predictions"), 
                        size=1.2, alpha = 0.6, colour="red") +
              
              geom_point(data=Beads_selected[[i]][[j]],
                         aes(x=1:nrow(Beads_selected[[i]][[j]]), y=Beads, colour=factor(Beads)),
                         size=3, show.legend = FALSE) + 
              
              geom_point(data=Responses_selected[[i]][[j]], 
                         aes(x=1:nrow(Responses_selected[[i]][[j]]), y=Responses),
                         size=1.5, show.legend = FALSE) +
              
              # Plot learning rate for AR1 models     
             {if (!(length(Learning_rate) == 0) & Analyses_nos[i] > 10){
               geom_line(aes(x=1:nrow(Learning_rate_selected[[i]][[j]]), y=LR, colour="Learning rate"), 
                         size=1, colour = "cornflowerblue", data=Learning_rate_selected[[i]][[j]])}}+
              
              theme(legend.position="bottom")+
              
              xlab("Bead index")+
              ylab("Responses (jar probability estimate)")+
              scale_x_continuous(breaks = seq(0, length(x_axes[[i]][[1]]), 1))+
              coord_cartesian(ylim=c(0,1))+
              scale_y_continuous(breaks = seq(0, 1, 0.1))+
              
              ggtitle(paste(sprintf("S %g, A %g; Fit (BOOC) = %g (smaller is better)\n", 
                                    Subjects[j], Analyses_nos[i], Fit_BOOC_subject[[i]][j]),
                            sprintf("Posteriors: Om2=%g; Om3=%g, Nu=%g; M2=%g; M3=%g; Phi2=%g; Phi3=%g",
                                    signif(Om2_vector[[i]][Subjects[j], 2], digits=3), 
                                    signif(Om3_vector[[i]][Subjects[j], 2], digits=3), 
                                    
                                    signif(Nu_vector[[i]][Subjects[j], 2], digits=3),
                                    
                                    signif(M2_vector[[i]][Subjects[j], 2], digits=3), 
                                    signif(M3_vector[[i]][Subjects[j], 2], digits=3), 
                                    
                                    signif(Phi2_vector[[i]][Subjects[j], 2], digits=3),
                                    signif(Phi3_vector[[i]][Subjects[j], 2], digits=3)
                                    ) ) ) +
              theme(plot.title = element_text(size = 12)) 
      
            )# print()
    
    } 
  }
        
} # if(Plot_subj == TRUE)
  
```

#### Box & density plots of parameter posteriors

```{r  echo = FALSE, results = 'asis', warning=FALSE, message=FALSE, cache=F}

if (Do_plots == TRUE){

for (i in seq(Om2_vector)){
  levels(Sa2_vector[[i]]$Group) <- gsub(" ", "\n", levels(Sa2_vector[[i]]$Group))
  levels(Om2_vector[[i]]$Group) <- gsub(" ", "\n", levels(Om2_vector[[i]]$Group))
  # levels(Om3_vector[[i]]$Group) <- gsub(" ", "\n", levels(Om3_vector[[i]]$Group))
  levels(Nu_vector[[i]]$Group) <- gsub(" ", "\n", levels(Nu_vector[[i]]$Group))
  levels(M2_vector[[i]]$Group) <- gsub(" ", "\n", levels(M2_vector[[i]]$Group))
  # levels(M3_vector[[i]]$Group) <- gsub(" ", "\n", levels(M3_vector[[i]]$Group))
  levels(Phi2_vector[[i]]$Group) <- gsub(" ", "\n", levels(Phi2_vector[[i]]$Group))
  # levels(Phi3_vector[[i]]$Group) <- gsub(" ", "\n", levels(Phi3_vector[[i]]$Group))
}
  
Title_size <- 7  
Base_size <- 7
  
# Box plot
for (i in 1:length(Analyses_nos)){
# tryCatch({x11()}, error = function(e) {quartz()}, warning = function(w){quartz()}) # New window
  Sa2_box <- ggplot(Sa2_vector[[i]], aes(Group, Sa2_vector))+
      geom_boxplot(aes(colour = Group), size = 0.5)+
      theme(plot.title = element_text(size = Title_size))+
      ggtitle("Sa2")+ 
      labs(x = "Group", y = "Sa2 posteriors")+ theme_grey(base_size = Base_size)
  
  Om2_box <- ggplot(Om2_vector[[i]], aes(Group, Om2_vector))+
    geom_boxplot(aes(colour = Group), size = 0.5)+
    theme(plot.title = element_text(size = Title_size))+
    ggtitle("Om2")+ 
    labs(x = "Group", y = "Om2 posteriors")+ theme_grey(base_size = Base_size)
    # scale_x_discrete(limits = levels(Group))
  # Om3_box <- ggplot(Om3_vector[[i]], aes(Group, Om3_vector))+
  #   geom_boxplot(aes(colour = Group), size = 0.5)+
  #   theme(plot.title = element_text(size = Title_size))+
  #   ggtitle("Om3")+
  #   labs(x = "Group", y = "Om3 posteriors") + theme_grey(base_size = Base_size)
  #   # scale_x_discrete(limits = levels(Group))
  
  Nu_box <- ggplot(Nu_vector[[i]], aes(Group, Nu_vector))+
    geom_boxplot(aes(colour = Group), size = 0.5)+
    theme(plot.title = element_text(size = Title_size))+
    ggtitle("log(Nu)")+
    labs(x = "Group", y = "Nu posteriors") + theme_grey(base_size = Base_size)
  
  M2_box <- ggplot(M2_vector[[i]], aes(Group, M2_vector))+
    geom_boxplot(aes(colour = Group), size = 0.5)+
    theme(plot.title = element_text(size = Title_size))+
    ggtitle("M2")+
    labs(x = "Group", y = "M2 posteriors") + theme_grey(base_size = Base_size)
    # scale_x_discrete(limits = levels(Group))
  # M3_box <- ggplot(M3_vector[[i]], aes(Group, M3_vector))+
  #   geom_boxplot(aes(colour = Group), size = 0.5)+
  #   theme(plot.title = element_text(size = Title_size))+
  #   ggtitle("M3")+
  #   labs(x = "Group", y = "M3 posteriors") + theme_grey(base_size = Base_size)
  #   # scale_x_discrete(limits = levels(Group))
  # 
  Phi2_box <- ggplot(Phi2_vector[[i]], aes(Group, Phi2_vector))+
    geom_boxplot(aes(colour = Group), size = 0.5)+
    theme(plot.title = element_text(size = Title_size))+
    ggtitle("Phi2")+
    labs(x = "Group", y = "Phi2 posteriors") + theme_grey(base_size = Base_size)
  # Phi3_box <- ggplot(Phi3_vector[[i]], aes(Group, Phi3_vector))+
  #   geom_boxplot(aes(colour = Group), size = 0.5)+
  #   theme(plot.title = element_text(size = Title_size))+
  #   ggtitle("Phi3")+
  #   labs(x = "Group", y = "Phi3 posteriors") + theme_grey(base_size = Base_size)
  
    Box_plots <- c(Sa2_box, Om2_box, Nu_box, M2_box, Phi2_box)
    N_box_plots <- length(Box_plots)/9
    N_col <- ceiling(N_box_plots/2)
    N_row <- floor(N_box_plots/2)
  
  grid.arrange(Sa2_box+theme(legend.position="none"),
               Om2_box+theme(legend.position="none"),
               # Om3_box+theme(legend.position="none"),
               Nu_box+theme(legend.position="none"),
               M2_box+theme(legend.position="none"),
               # M3_box+theme(legend.position="none"), 
               Phi2_box+theme(legend.position="none"),
               # Phi3_box+theme(legend.position="none"), 
               ncol=N_col, nrow=N_row,
               top = sprintf("Sa2, Om2, log(Nu), M2 & Phi2 posteriors; A %d", 
                               Analyses_nos[i]), 
               heights=rep(5, N_row), widths=rep(3, N_col))
}

# Density plots
  
  Alpha <- .3
  Size <- .5
  
for (i in 1:length(Analyses_nos)){
# tryCatch({x11()}, error = function(e) {quartz()}, warning = function(w){quartz()}) # New window
    Sa2_dens <- ggplot(Sa2_vector[[i]], aes(Sa2_vector))+
      geom_density(aes(fill = Group), size = Size, alpha=Alpha)+
      theme(plot.title = element_text(size = Title_size))+
      ggtitle("Sa2") + theme_grey(base_size = Base_size)
    
    Om2_dens <- ggplot(Om2_vector[[i]], aes(Om2_vector))+
      geom_density(aes(fill = Group), size = Size, alpha=Alpha)+
      theme(legend.position="bottom", plot.title = element_text(size = Title_size))+
      ggtitle("Om2") + theme_grey(base_size = Base_size)
    
    # Om3_dens <- ggplot(Om3_vector[[i]], aes(Om3_vector))+
    #   geom_density(aes(fill = Group, colour = Group), size = 0.5, alpha=0.3)+
    #   theme(plot.title = element_text(size = Title_size))+
    #   ggtitle("Om3") + theme_grey(base_size = Base_size)
    
    Nu_dens <- ggplot(Nu_vector[[i]], aes(Nu_vector))+
      geom_density(aes(fill = Group), size = Size, alpha=Alpha)+
      theme(plot.title = element_text(size = Title_size))+
      ggtitle("log(Nu)") + theme_grey(base_size = Base_size)
    
    M2_dens <- ggplot(M2_vector[[i]], aes(M2_vector))+
      geom_density(aes(fill = Group), size = Size, alpha=Alpha)+
      theme(plot.title = element_text(size = Title_size))+
      ggtitle("M2") + theme_grey(base_size = Base_size)
    # M3_dens <- ggplot(M3_vector[[i]], aes(M3_vector))+
    #   geom_density(aes(fill = Group, colour = Group), size = 0.5, alpha=0.3)+
    #   theme(plot.title = element_text(size = Title_size))+
    #   ggtitle("M3") + theme_grey(base_size = Base_size)
    
    Phi2_dens <- ggplot(Phi2_vector[[i]], aes(Phi2_vector))+
      geom_density(aes(fill = Group), size = Size, alpha=Alpha)+
      theme(plot.title = element_text(size = Title_size))+
      ggtitle("Phi2") + theme_grey(base_size = Base_size)
    # Phi3_dens <- ggplot(Phi3_vector[[i]], aes(Phi3_vector))+
    #   geom_density(aes(fill = Group, colour = Group), size = 0.5, alpha=0.3)+
    #   theme(plot.title = element_text(size = Title_size))+
    #   ggtitle("Phi3") + theme_grey(base_size = Base_size)
    
    Dens_plots <- c(Sa2_dens, Om2_dens, Nu_dens, M2_dens, Phi2_dens)
    N_dens_plots <- length(Dens_plots)/9
    N_col <- ceiling(N_dens_plots/2)
    N_row <- floor(N_dens_plots/2)
    My_legend <- g_legend(Om2_dens)
    
    grid.arrange(Sa2_dens+theme(legend.position="none"),
                 Om2_dens+theme(legend.position="none"),
                 # Om3_dens+theme(legend.position="none"), 
                 Nu_dens+theme(legend.position="none"), 
                 M2_dens+theme(legend.position="none"),
                 # M3_dens+theme(legend.position="none"), 
                 Phi2_dens+theme(legend.position="none"),
                 # Phi3_dens+theme(legend.position="none"),
                 ncol=N_col, nrow=N_row, 
                 My_legend,
                 top = sprintf("Sa2, Om2, log(Nu), M2 & Phi2 posteriors; A %d", 
                               Analyses_nos[i]), 
                 heights=rep(5, N_row), widths=rep(3, N_col))
}

} # if (Do_plots == TRUE)

```






















