---
title: "Gilleen data behavioural analyses of PDG and beads tasks"
author: "Gary Napier"
date: "12 August 2016"
output: html_document
---

<!-- misc setup -->

```{r, echo=F, warning=FALSE, message=FALSE}

# Sources packages and custom functions
source("https://raw.githubusercontent.com/GaryNapier/Packages_functions/master/PACKAGES.R")

# GILLEEN DATA BEHAVIOURAL

# James original email - 15 June 

# Attached is the complete PDG and Beads data for the Healthy and Patients. There are 3 tabs, the PDG action for each round (1=compete, 2=cooperate); PDG trust (the rating of trust after each round (1=totally untrustworthy, 7 totally trustworthy, 4 unsure [i.e. 0 = totally untrustworthy, 1 = totally trustworthy, 0.5 = unsure])
# and Beads (1= definitely Jar A, 7=definitely Jar B; 4 unsure [i.e. 0 = definitely Jar A, 1 = definitely Jar B, 0.5 = unsure]). I hope this is clear.
# 
# As a reminder, for the PDG, A=mostly cooperative, D=mostly competitive, B=first half mostly cooperative switching to second half mostly competitive, and C vice versa). 

#####

# There are 3 datasets:
#   - PDG action for each round (1=compete, 2=cooperate); 
#   - PDG trust (the rating of trust after each round (1=totally untrustworthy, 
#     7 totally trustworthy, 4 unsure [i.e. 0 = totally untrustworthy, 1 = totally trustworthy, 
#     0.5 = unsure]) and
#   - Beads (1= definitely Jar A, 7=definitely Jar B; 4 unsure [i.e. 0 = definitely Jar A, 
#     1 = definitely Jar B, 0.5 = unsure]). 
#                                                                                                                                                                
# For the PDG, A=mostly cooperative, D=mostly competitive, B=first half mostly 
# cooperative switching to second half mostly competitive, and C vice versa). 

# p.s. there appears to be duplication of ID numbers for the patients but don't
# worry they are different - student confusion, but for data organisation on other
# files I'm leaving it as it is for now.

# set WD
tryCatch({
  setwd("U:/Gilleen_data")
}, error=function(e) {
  setwd("~/Dropbox/Gilleen_Analysis/For Gary")
})

# Misc
Bins <- 10
Alpha_hist <- .6
Alpha_dens <- .3
Alpha_line <- .3

Tasks <- c("PDG", "Beads")
Groups <- c("Healthy", "Patient")
N_tasks <- 2
N_groups <- 2

Blue <- "#F1F0FA"

Action <- c("Compete", "Cooperate")

# Set the default theme
theme_set(theme_grey())

#---------------------------------------------------------------------------------------
# Read in data
#---------------------------------------------------------------------------------------

Healthy_PDG   <- read.csv("Gilleen_healthy_PDG_trust.csv", header = TRUE)
Healthy_beads <- read.csv("Gilleen_healthy_beads.csv", header = TRUE)
Patient_PDG   <- read.csv("Gilleen_patient_PDG_trust.csv", header = TRUE)
Patient_beads <- read.csv("Gilleen_patient_beads.csv", header = TRUE)

# Clean Healthy_beads
Healthy_beads <- tryCatch({
  dplyr::select(Healthy_beads, -(X:X.11))
}, error=function(e){Healthy_beads})

N_subj_healthy <- nrow(Healthy_PDG)
N_subj_pat <- nrow(Patient_PDG)

# Healthy_PDG
# Healthy_beads
# Patient_PDG
# Patient_beads

#---------------------------------------------------------------------------------------
# Clean
#---------------------------------------------------------------------------------------

# Order by ID #
Healthy_PDG   <- Healthy_PDG[order(Healthy_PDG$ID),]
Healthy_beads <- Healthy_beads[order(Healthy_beads$ID),]
Patient_PDG   <- Patient_PDG[order(Patient_PDG$ID),]
Patient_beads <- Patient_beads[order(Patient_beads$ID),]

# Take out ID col & save as sep variable if needed
Healthy_ID <- Healthy_PDG[,1]
Patient_ID <- Patient_PDG[,1]

Healthy_PDG   <- Healthy_PDG[,-1]
Healthy_beads <- Healthy_beads[,-1]
Patient_PDG   <- Patient_PDG[,-1]
Patient_beads <- Patient_beads[,-1]

# Convert data to 0-1 scale
Healthy_PDG    <- (Healthy_PDG-1)/max(Healthy_PDG-1)
Healthy_beads  <- (Healthy_beads-1)/max(Healthy_beads-1)
Patient_PDG    <- (Patient_PDG-1)/max(Patient_PDG-1)
Patient_beads  <- (Patient_beads-1)/max(Patient_beads-1)

# Unique values on the standardised scale 
Values <- 0:6/6

# Sequences
Seq_A <-  c(1, 1, 0, 1, 1, 1, 0, 1, 1, 1)
Seq_B <-  c(1, 1, 1, 0, 1, 0, 0, 0, 1, 0)
Seq_C <-  c(0, 0, 0, 1, 0, 1, 1, 1, 0, 1)
Seq_D <-  c(0, 0, 1, 0, 0, 0, 1, 0, 0, 0)
Seq_PDG <- c(Seq_A, Seq_B, Seq_C, Seq_D)
Seq_beads <- c(Seq_D, Seq_C, Seq_B, Seq_A)

# Indices 
A_PDG_ind <- 1:10
B_PDG_ind <- 11:20
B_FH_PDG_ind <- 11:15
B_SH_PDG_ind <- 16:20
C_PDG_ind <- 21:30
C_FH_PDG_ind <- 21:25
C_SH_PDG_ind <- 26:30
D_PDG_ind <- 31:40

A_beads_ind <- D_PDG_ind
B_beads_ind <- C_PDG_ind
B_FH_beads_ind <- C_FH_PDG_ind
B_SH_beads_ind <- C_SH_PDG_ind
C_beads_ind <- B_PDG_ind
C_FH_beads_ind <- B_FH_PDG_ind
C_SH_beads_ind <- B_SH_PDG_ind
D_beads_ind <- A_PDG_ind

Seq_names <- c("A", "B first half", "B second half", "C first half", "C second half", "D")


#---------------------------------------------------------------------------------------
# Get stats
#---------------------------------------------------------------------------------------

# Get means
Healthy_PDG_mean    <- colMeans(Healthy_PDG)
Healthy_beads_mean  <- colMeans(Healthy_beads)
Patient_PDG_mean    <- colMeans(Patient_PDG)
Patient_beads_mean  <- colMeans(Patient_beads)

# Get medians 
Healthy_PDG_med    <- colMedians(Healthy_PDG)
Healthy_beads_med  <- colMedians(Healthy_beads)
Patient_PDG_med    <- colMedians(Patient_PDG)
Patient_beads_med  <- colMedians(Patient_beads)

Healthy_PDG_ster    <- std.error(Healthy_PDG)
Healthy_beads_ster <- std.error(Healthy_beads)
Patient_PDG_ster    <- std.error(Patient_PDG)
Patient_beads_ster  <- std.error(Patient_beads)

# Summarise data
# See http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)/
# Convert to long first
Healthy_PDG_long <- gather(Healthy_PDG, Sequence, Data, A:D.9)
Healthy_beads_long <- gather(Healthy_beads, Sequence, Data, A:D.9)
Patient_PDG_long <- gather(Patient_PDG, Sequence, Data, A:D.9)
Patient_beads_long <- gather(Patient_beads, Sequence, Data, A:D.9)

Healthy_PDG_sum <- summarySE(Healthy_PDG_long, measurevar="Data", groupvars="Sequence")
Healthy_beads_sum <- summarySE(Healthy_beads_long, measurevar="Data", groupvars="Sequence")
Patient_PDG_sum <- summarySE(Patient_PDG_long, measurevar="Data", groupvars="Sequence")
Patient_beads_sum <- summarySE(Patient_beads_long, measurevar="Data", groupvars="Sequence")


```

### Three datasets:
- PDG action for each round (compete /cooperate); 
- PDG trust rating (0 = totally untrustworthy, 1 = totally trustworthy, 0.5 = unsure) and 
- Beads (0 = definitely jar A, 1 = definitely jar B, 0.5 = unsure).

### Four sequences:
- PDG task: Seq A = mostly cooperative, Seq D = mostly competitive, Seq B = first half mostly cooperative switching to second half mostly competitive, and Seq C vice versa. 
- Beads task: As the PDG task except 'comptetitive' and 'cooperative' replaced by 'Jar A' and 'Jar B'

### Questions - Are there group differences in:
1. First half ‘draws to certainty (DTC)’ - How many trials until subjects reach maximum certainty (1 or 0) in the first half of either task. Also, how many subjects, as a proportion of group numbers, reach maximum certainty at which trial indeces?

2. Second half DTC - How many trials until subjects reach maximum certainty after the change 
of jar/trustworthiness in Seq B and Seq C only.

3. The initial decision whether to cooperate/compete in the PDG in all four sequences.

4. The average trust ratings on each trial the same in Seq A and Seq D ('mostly cooperate', 'mostly compete', respectively).

**-------------------------------------------------------------------------------------------------**

### Plots of mean responses, PDG and beads tasks

```{r echo=F, warning=FALSE, message=FALSE}

#---------------------------------------------------------------------------------------
# Plots
#---------------------------------------------------------------------------------------

# Plot PDG
Plot_PDG <- function(){
  ggplot(Healthy_PDG_sum, aes(x=Sequence, y=Data, group=1)) +
    geom_errorbar(aes(ymin=Data-se, ymax=Data+se), width=.2)+
    geom_line(colour = "red", size = 1, alpha=.7)+
    geom_errorbar(data=Patient_PDG_sum, aes(ymin=Data-se, ymax=Data+se), width=.2)+
    geom_line(data=Patient_PDG_sum, aes(x=Sequence, y=Data), colour = "blue", size = 1, alpha=.7)+
    geom_point(data=data.frame(Seq_PDG),
               aes(x=1:length(Seq_PDG), y=Seq_PDG, colour=factor(Seq_PDG)),
               size=3, show.legend = FALSE)+
    scale_x_discrete(labels = Seq_PDG)+
    expand_limits(x = c(1, length(Seq_PDG)+3))+
    scale_y_continuous(breaks = seq(0,1,0.1), limits = c(-0.1, 1.1))+
    ylab("Trustworthiness rating")+
    geom_vline(xintercept = c(10.5, 20.5, 30.5), linetype = "longdash")+
    geom_hline(yintercept = Values, alpha=Alpha_line)+
    annotate("text", x = c(5, 15, 25, 35), y=0.1, label = c("A", "B", "C", "D"), fontface = "bold")+
    annotate("text", x = length(Seq_PDG)/2, y=c(-0.1, 1.1), label=c("Compete", "Cooperate"))+
    annotate("text", x=length(Seq_PDG)+1, y=Values, label=as.character(1:7), size=3 )+
    annotate("text", x = length(Seq_PDG)+2, y=0.5, label="Original scale", angle=270)+
    ggtitle("Mean PDG data, healthy (red) & patient (blue).\n0 = totally untrustworthy, 1 = totally trustworthy")+
    theme_grey()
}

Plot_PDG()
#

# Plot beads
Plot_beads <- function() {
  ggplot(Healthy_beads_sum, aes(x=Sequence, y=Data, group=1)) +
    geom_errorbar(aes(ymin=Data-se, ymax=Data+se), width=.2)+
    geom_line(colour = "red", size = 1, alpha=.7)+
    geom_errorbar(data=Patient_beads_sum, aes(ymin=Data-se, ymax=Data+se), width=.2)+
    geom_line(data=Patient_beads_sum, aes(x=Sequence, y=Data), colour = "blue", size = 1, alpha=.7)+
    geom_point(data=data.frame(Seq_beads),
               aes(x=1:length(Seq_beads), y=Seq_beads, colour=factor(Seq_beads)),
               size=3, show.legend = FALSE) +
    scale_x_discrete(labels = Seq_beads)+
    expand_limits(x = c(1, length(Seq_PDG)+3))+
    scale_y_continuous(breaks = seq(0,1,0.1), limits = c(-0.1, 1.1))+
    ylab("Confidence in jar")+
    geom_vline(xintercept = c(10.5, 20.5, 30.5), linetype = "longdash")+
    geom_hline(yintercept = Values, alpha=Alpha_line)+
    annotate("text", x = c(5, 15, 25, 35), y=0.1, label = c("D", "C", "B", "A"), fontface = "bold")+
    annotate("text", x = length(Seq_PDG)/2, y=c(-0.1, 1.1), label=c("Jar A", "Jar B"))+
    annotate("text", x=length(Seq_PDG)+1, y=Values, label=as.character(1:7), size=3 )+
    annotate("text", x = length(Seq_PDG)+2, y=0.5, label="Original scale", angle=270)+
    ggtitle("Mean beads data, healthy (red) & patient (blue). \n0 = definitely Jar A, 1 = definitely Jar B")+
    theme_grey()
}

Plot_beads()


```

<!--##### Histograms of mean responses on each trial, PDG and beads tasks-->

```{r echo=F, warning=FALSE, message=FALSE}
# Histograms of mean responses on each trial (healthy PDG/beads, patient PDG/beads)
# x11()
# Hist_healthy_PDG <- ggplot(data= data.frame(Healthy_PDG_mean), aes(x=Healthy_PDG_mean))+
#   geom_histogram(aes(y=..count..),
#                  bins =Bins, colour="gray", fill="blue", alpha=Alpha_hist)+
#   coord_cartesian(xlim=c(0,1), ylim=c(0,10))+
#   scale_x_continuous(breaks = seq(0, 1, 0.1))+
#   scale_y_continuous(breaks = seq(0, 10, 1))+
#   ggtitle("Healthy_PDG_mean")+
#   labs(x="Responses (jar probability estimate)", y="Count")+
#   geom_density(alpha=Alpha_dens, fill="red")+
#   theme_grey()
# Hist_patient_PDG <- ggplot(data= data.frame(Patient_PDG_mean), aes(x=Patient_PDG_mean))+
#   geom_histogram(aes(y=..count..),
#                  bins =Bins, colour="gray", fill="blue", alpha=Alpha_hist)+
#   coord_cartesian(xlim=c(0,1), ylim=c(0,10))+
#   scale_x_continuous(breaks = seq(0, 1, 0.1))+
#   scale_y_continuous(breaks = seq(0, 10, 1))+
#   ggtitle("Patient_PDG_mean")+
#   labs(x="Responses (jar probability estimate)", y="Count")+
#   geom_density(alpha=Alpha_dens, fill="red")+
#   theme_grey()
# Hist_healthy_beads <- ggplot(data= data.frame(Healthy_beads_mean), aes(x=Healthy_beads_mean))+
#   geom_histogram(aes(y=..count..),
#                  bins =Bins, colour="gray", fill="blue", alpha=Alpha_hist)+
#   coord_cartesian(xlim=c(0,1), ylim=c(0,10))+
#   scale_x_continuous(breaks = seq(0, 1, 0.1))+
#   scale_y_continuous(breaks = seq(0, 10, 1))+
#   ggtitle("Healthy_beads_mean")+
#   labs(x="Responses (jar probability estimate)", y="Count")+
#   geom_density(alpha=Alpha_dens, fill="red")+
#   theme_grey()
# Hist_patient_beads <- ggplot(data= data.frame(Patient_beads_mean), aes(x=Patient_beads_mean))+
#   geom_histogram(aes(y=..count..),
#                  bins =Bins, colour="gray", fill="blue", alpha=Alpha_hist)+
#   coord_cartesian(xlim=c(0,1), ylim=c(0,10))+
#   scale_x_continuous(breaks = seq(0, 1, 0.1))+
#   scale_y_continuous(breaks = seq(0, 10, 1))+
#   ggtitle("Patient_beads_mean")+
#   labs(x="Responses (jar probability estimate)", y="Count")+
#   geom_density(alpha=Alpha_dens, fill="red")+
#   theme_grey()
# grid.arrange(Hist_healthy_PDG, Hist_patient_PDG, Hist_healthy_beads,
#              Hist_patient_beads, ncol=2, nrow=2, 
#              top=textGrob("Histograms of mean responses on each trial"))


```

**-------------------------------------------------------------------------------------------------**


#### 1a. First half ‘draws to certainty (DTC)’ - How many trials until subjects reach maximum certainty (0 or 1; 1 or 7 in original Likert scale) in the first half of both tasks.

##### NB - if subjects took more than 5 trials to certainty, this was counted as '5', so there were **at least** 5 trials to certainty. 

<!-- # How many subjects make a DTC at which indeces? - Get data -->
```{r echo=F, warning=FALSE, message=FALSE}

# SETUP HOW MANY 
# How many subjects make a DTC at which indeces? - Get data
FH_1 <- 1:5
FH_2 <- 11:15
FH_3 <- 21:25
FH_4 <- 31:35
Draws <- c("Draw_1", "Draw_2", "Draw_3", "Draw_4", "Draw_5")

# PDG 
Healthy_PDG_A <- Healthy_PDG[FH_1] # Blue jar (1)
Healthy_PDG_B <- Healthy_PDG[FH_2] # Blue 1st half (1), Red 2nd (0)
Healthy_PDG_C <- Healthy_PDG[FH_3] # Red 1st (0), Blue 2nd (1)
Healthy_PDG_D <- Healthy_PDG[FH_4] # Red jar

Patient_PDG_A <- Patient_PDG[FH_1]
Patient_PDG_B <- Patient_PDG[FH_2]
Patient_PDG_C <- Patient_PDG[FH_3]
Patient_PDG_D <- Patient_PDG[FH_4]

# How many subj reached DTC at which bead index? PDG
How_many_DTC_He_A <- sapply(Healthy_PDG_A, function(x) sum(x==1)  ) # Blue jar (1)
How_many_DTC_He_B <- sapply(Healthy_PDG_B, function(x) sum(x==1)  ) # Blue 1st half (1), Red 2nd (0)
How_many_DTC_He_C <- sapply(Healthy_PDG_C, function(x) sum(x==0)  ) # Red 1st (0), Blue 2nd (1)
How_many_DTC_He_D <- sapply(Healthy_PDG_D, function(x) sum(x==0)  ) # Red jar (0)

How_many_DTC_healthy_PDG <- data.frame(Draws=Draws,
                                       Proportion_subjects = colMeans(rbind(How_many_DTC_He_A, 
                                                                How_many_DTC_He_B, 
                                                                How_many_DTC_He_C, 
                                                                How_many_DTC_He_D) / N_subj_healthy ))

How_many_pat_A <- sapply(Patient_PDG_A, function(x) sum(x==1)  )
How_many_pat_B <- sapply(Patient_PDG_B, function(x) sum(x==1)  )
How_many_pat_C <- sapply(Patient_PDG_C, function(x) sum(x==0)  )
How_many_pat_D <- sapply(Patient_PDG_D, function(x) sum(x==0)  )

How_many_DTC_pat_PDG <- data.frame(Draws=Draws,
                                   Proportion_subjects = colMeans(rbind(How_many_pat_A, 
                                                            How_many_pat_B,
                                                            How_many_pat_C,
                                                            How_many_pat_D) / N_subj_pat ))

# BEADS
Healthy_beads_A <- Healthy_beads[FH_1]
Healthy_beads_B <- Healthy_beads[FH_2]
Healthy_beads_C <- Healthy_beads[FH_3]
Healthy_beads_D <- Healthy_beads[FH_4]

Patient_beads_A <- Patient_beads[FH_1]
Patient_beads_B <- Patient_beads[FH_2]
Patient_beads_C <- Patient_beads[FH_3]
Patient_beads_D <- Patient_beads[FH_4]

# How many subj reached DTC at which bead index? Beads
How_many_DTC_He_beads_A <- sapply(Healthy_beads_A, function(x) sum(x==0)  ) # Blue jar (1)
How_many_DTC_He_beads_B <- sapply(Healthy_beads_B, function(x) sum(x==0)  ) # Blue 1st half (1), Red 2nd (0)
How_many_DTC_He_beads_C <- sapply(Healthy_beads_C, function(x) sum(x==1)  ) # Red 1st (0), Blue 2nd (1)
How_many_DTC_He_beads_D <- sapply(Healthy_beads_D, function(x) sum(x==1)  ) # Red jar (0)

How_many_DTC_healthy_beads <- data.frame(Draws=Draws, 
                                         Proportion_subjects = colMeans(rbind(How_many_DTC_He_beads_A,
                                                                  How_many_DTC_He_beads_B, 
                                                                  How_many_DTC_He_beads_C,
                                                                  How_many_DTC_He_beads_D) / N_subj_healthy))

How_many_DTC_pat_beads_A <- sapply(Patient_beads_A, function(x) sum(x==1)  )
How_many_DTC_pat_beads_B <- sapply(Patient_beads_B, function(x) sum(x==1)  )
How_many_DTC_pat_beads_C <- sapply(Patient_beads_C, function(x) sum(x==0)  )
How_many_DTC_pat_beads_D <- sapply(Patient_beads_D, function(x) sum(x==0)  )

How_many_DTC_pat_beads <- data.frame(Draws=Draws, 
                                     Proportion_subjects = colMeans(rbind(How_many_DTC_pat_beads_A, 
                                                              How_many_DTC_pat_beads_B, 
                                                              How_many_DTC_pat_beads_C,
                                                              How_many_DTC_pat_beads_D) / N_subj_pat ))

```

<!-- SETUP NO OF TRIALS TO 0/1 / 1/7 -->
```{r echo=F, warning=FALSE, message=FALSE}
# SETUP NO OF TRIALS TO 0/1 / 1/7

# Healthy PDG
Healthy_PDG_DTC_A <- apply(Healthy_PDG_A[,c(1:5)], 1, function(x) min(which(x==1)))
Healthy_PDG_DTC_A <- ifelse(Healthy_PDG_DTC_A==Inf, 5, Healthy_PDG_DTC_A)
Healthy_PDG_DTC_B <- apply(Healthy_PDG_B[,c(1:5)], 1, function(x) min(which(x==1)))
Healthy_PDG_DTC_B <- ifelse(Healthy_PDG_DTC_B==Inf, 5, Healthy_PDG_DTC_B)
Healthy_PDG_DTC_C <- apply(Healthy_PDG_C[,c(1:5)], 1, function(x) min(which(x==0)))
Healthy_PDG_DTC_C <- ifelse(Healthy_PDG_DTC_C==Inf, 5, Healthy_PDG_DTC_C)
Healthy_PDG_DTC_D <- apply(Healthy_PDG_D[,c(1:5)], 1, function(x) min(which(x==0)))
Healthy_PDG_DTC_D <- ifelse(Healthy_PDG_DTC_D==Inf, 5, Healthy_PDG_DTC_D)

DTC_healthy_PDG <- (sum(c(Healthy_PDG_DTC_A, Healthy_PDG_DTC_B, 
                          Healthy_PDG_DTC_C, Healthy_PDG_DTC_D)) / 4) / N_subj_healthy

# Patient PDG
Pat_PDG_DTC_A <- apply(Patient_PDG_A[,c(1:5)], 1, function(x) min(which(x==1)))
Pat_PDG_DTC_A <- ifelse(Pat_PDG_DTC_A==Inf, 5, Pat_PDG_DTC_A)
Pat_PDG_DTC_B <- apply(Patient_PDG_B[,c(1:5)], 1, function(x) min(which(x==1)))
Pat_PDG_DTC_B <- ifelse(Pat_PDG_DTC_B==Inf, 5, Pat_PDG_DTC_B)
Pat_PDG_DTC_C <- apply(Patient_PDG_C[,c(1:5)], 1, function(x) min(which(x==0)))
Pat_PDG_DTC_C <- ifelse(Pat_PDG_DTC_C==Inf, 5, Pat_PDG_DTC_C)
Pat_PDG_DTC_D <- apply(Patient_PDG_D[,c(1:5)], 1, function(x) min(which(x==0)))
Pat_PDG_DTC_D <- ifelse(Pat_PDG_DTC_D==Inf, 5, Pat_PDG_DTC_D)

DTC_pat_PDG <- (sum(c(Pat_PDG_DTC_A, Pat_PDG_DTC_B,
                      Pat_PDG_DTC_C, Pat_PDG_DTC_D)) / 4) / N_subj_pat

# Healthy beads
Healthy_beads_DTC_A <- apply(Healthy_beads_A[,c(1:5)], 1, function(x) min(which(x==1)))
Healthy_beads_DTC_A <- ifelse(Healthy_beads_DTC_A==Inf, 5, Healthy_beads_DTC_A)
Healthy_beads_DTC_B <- apply(Healthy_beads_B[,c(1:5)], 1, function(x) min(which(x==1)))
Healthy_beads_DTC_B <- ifelse(Healthy_beads_DTC_B==Inf, 5, Healthy_beads_DTC_B)
Healthy_beads_DTC_C <- apply(Healthy_beads_C[,c(1:5)], 1, function(x) min(which(x==0)))
Healthy_beads_DTC_C <- ifelse(Healthy_beads_DTC_C==Inf, 5, Healthy_beads_DTC_C)
Healthy_beads_DTC_D <- apply(Healthy_beads_D[,c(1:5)], 1, function(x) min(which(x==0)))
Healthy_beads_DTC_D <- ifelse(Healthy_beads_DTC_D==Inf, 5, Healthy_beads_DTC_D)

DTC_healthy_beads <- (sum(c(Healthy_beads_DTC_A, Healthy_beads_DTC_B,
                            Healthy_beads_DTC_C, Healthy_beads_DTC_D)) / 4) / N_subj_healthy

# Patient beads
Pat_beads_DTC_A <- apply(Patient_beads_A[,c(1:5)], 1, function(x) min(which(x==1)))
Pat_beads_DTC_A <- ifelse(Pat_beads_DTC_A==Inf, 5, Pat_beads_DTC_A)
Pat_beads_DTC_B <- apply(Patient_beads_B[,c(1:5)], 1, function(x) min(which(x==1)))
Pat_beads_DTC_B <- ifelse(Pat_beads_DTC_B==Inf, 5, Pat_beads_DTC_B)
Pat_beads_DTC_C <- apply(Patient_beads_C[,c(1:5)], 1, function(x) min(which(x==0)))
Pat_beads_DTC_C <- ifelse(Pat_beads_DTC_C==Inf, 5, Pat_beads_DTC_C)
Pat_beads_DTC_D <- apply(Patient_beads_D[,c(1:5)], 1, function(x) min(which(x==0)))
Pat_beads_DTC_D <- ifelse(Pat_beads_DTC_D==Inf, 5, Pat_beads_DTC_D)

DTC_pat_beads <- (sum(c(Pat_beads_DTC_A, Pat_beads_DTC_B,
                        Pat_beads_DTC_C, Pat_beads_DTC_D)) / 4) / N_subj_pat

DTC <- signif(c(DTC_healthy_PDG, DTC_pat_PDG, DTC_healthy_beads, DTC_pat_beads), digits=3)

htmlTable(DTC, cgroup=Tasks, n.cgroup= rep(2, N_tasks), header=rep(Groups, 2), 
          align = c("c", "|"), align.header=c("c", "|"), col.columns=c("none", Blue), 
          caption = "Average draws to certainty over first half of all sequences")

# Plot:
# PDG
DTC_healthy_PDG_all <- c(Healthy_PDG_DTC_A, Healthy_PDG_DTC_B, Healthy_PDG_DTC_C, Healthy_PDG_DTC_D)
DTC_pat_PDG_all <- c(Pat_PDG_DTC_A, Pat_PDG_DTC_B, Pat_PDG_DTC_C, Pat_PDG_DTC_D)

DTC_healthy_PDG_all_table <- data.frame((table(DTC_healthy_PDG_all)/N_subj_healthy)/4)
DTC_pat_PDG_all_table <- data.frame((table(DTC_pat_PDG_all)/N_subj_pat)/4)

colnames(DTC_healthy_PDG_all_table) <- c("Draw", "Freq")
colnames(DTC_pat_PDG_all_table) <- c("Draw", "Freq")

Number_DTC_PDG <- ggplot(NULL, aes(Draw, Freq))+
  theme_grey()+
  stat_summary_bin(aes(fill = "Healthy"),
                   data=DTC_healthy_PDG_all_table,
                   fun.y="sum", geom = "bar", alpha=.5)+
  stat_summary_bin(aes(fill= "Patient"), 
                   data=DTC_pat_PDG_all_table, 
                   fun.y="sum", geom = "bar", alpha=.5)+
  theme(legend.position="bottom")+
  ggtitle("Proportion of subjects reaching DTC by trial number, all seqs, PDG")+
  scale_y_continuous(limits=c(0, 1))
Number_DTC_PDG

# Beads 
DTC_healthy_beads_all <- c(Healthy_beads_DTC_A, Healthy_beads_DTC_B, Healthy_beads_DTC_C, Healthy_beads_DTC_D)
DTC_pat_beads_all <- c(Pat_beads_DTC_A, Pat_beads_DTC_B, Pat_beads_DTC_C, Pat_beads_DTC_D)

DTC_healthy_beads_all_table <- data.frame((table(DTC_healthy_beads_all)/N_subj_healthy)/4)
DTC_pat_beads_all_table <- data.frame((table(DTC_pat_beads_all)/N_subj_pat)/4)

colnames(DTC_healthy_beads_all_table) <- c("Draw", "Freq")
colnames(DTC_pat_beads_all_table) <- c("Draw", "Freq")

Number_DTC_beads <- ggplot(NULL, aes(Draw, Freq))+
  theme_grey()+
  stat_summary_bin(aes(fill = "Healthy"),
                   data=DTC_healthy_beads_all_table,
                   fun.y="sum", geom = "bar", alpha=.5)+
  stat_summary_bin(aes(fill= "Patient"), 
                   data=DTC_pat_beads_all_table, 
                   fun.y="sum", geom = "bar", alpha=.5)+
  theme(legend.position="bottom")+
  ggtitle("Proportion of subjects reaching DTC by trial number, beads")+
  scale_y_continuous(limits=c(0, 1))
Number_DTC_beads
```

##### Group statistics of final certainty ratings for each seq, PDG and beads
<!-- Group stats on the final certainty scores in each sequence? -->
```{r echo=F, warning=FALSE, message=FALSE}
#---------------------------------------------------------------------------------------------
# Group stats on the final certainty scores in each sequence?
#---------------------------------------------------------------------------------------------

# Get final cert scores

# PDG - cert scores
Healthy_PDG_A_cert <- apply(Healthy_PDG[A_PDG_ind], 1, max)
# Healthy_PDG_B_cert <- apply(Healthy_PDG[B_PDG_ind], 1, min)
Healthy_PDG_B_FH_cert <- apply(Healthy_PDG[B_FH_PDG_ind], 1, max)
Healthy_PDG_B_SH_cert <- apply(Healthy_PDG[B_SH_PDG_ind], 1, min)
# Healthy_PDG_C_cert <- apply(Healthy_PDG[C_PDG_ind], 1, max)
Healthy_PDG_C_FH_cert <- apply(Healthy_PDG[C_FH_PDG_ind], 1, min)
Healthy_PDG_C_SH_cert <- apply(Healthy_PDG[C_SH_PDG_ind], 1, max)
Healthy_PDG_D_cert <- apply(Healthy_PDG[D_PDG_ind], 1, min)

Pat_PDG_A_cert <- apply(Patient_PDG[A_PDG_ind], 1, max)
# Pat_PDG_B_cert <- apply(Patient_PDG[B_PDG_ind], 1, min)
Pat_PDG_B_FH_cert <- apply(Patient_PDG[B_FH_PDG_ind], 1, max)
Pat_PDG_B_SH_cert <- apply(Patient_PDG[B_SH_PDG_ind], 1, min)
# Pat_PDG_C_cert <- apply(Patient_PDG[C_PDG_ind], 1, max)
Pat_PDG_C_FH_cert <- apply(Patient_PDG[C_FH_PDG_ind], 1, min)
Pat_PDG_C_SH_cert <- apply(Patient_PDG[C_SH_PDG_ind], 1, max)
Pat_PDG_D_cert <- apply(Patient_PDG[D_PDG_ind], 1, min)

# Means
Means <- c(mean(Healthy_PDG_A_cert), mean(Pat_PDG_A_cert), mean(Healthy_PDG_B_FH_cert), mean(Pat_PDG_B_FH_cert), mean(Healthy_PDG_B_SH_cert), mean(Pat_PDG_B_SH_cert), mean(Healthy_PDG_C_FH_cert), mean(Pat_PDG_C_FH_cert), mean(Healthy_PDG_C_SH_cert), mean(Pat_PDG_C_SH_cert), mean(Healthy_PDG_D_cert), mean(Pat_PDG_D_cert))
dim(Means) <- c(2, 6)
Means <- t(Means)
colnames(Means) <- c("Healthy mean", "Pat mean")

# Test PDG diffs in cert scores
Test_cert_A <- t.test(Healthy_PDG_A_cert, Pat_PDG_A_cert)
Test_cert_B_FH <- t.test(Healthy_PDG_B_FH_cert, Pat_PDG_B_FH_cert)
Test_cert_B_SH <- t.test(Healthy_PDG_B_SH_cert, Pat_PDG_B_SH_cert)
Test_cert_C_FH <- t.test(Healthy_PDG_C_FH_cert, Pat_PDG_C_FH_cert)
Test_cert_C_SH <- t.test(Healthy_PDG_C_SH_cert, Pat_PDG_C_SH_cert)
Test_cert_D <- t.test(Healthy_PDG_D_cert, Pat_PDG_D_cert)

# Put together table
Stats <- list(Test_cert_A, Test_cert_B_FH, Test_cert_B_SH, Test_cert_C_FH, Test_cert_C_SH, Test_cert_D)
names(Stats) <- Seq_names
Stats <- lapply(Stats, function(x) {c(x$statistic, x$parameter, x$p.value)})
Stats <- data.frame(cbind(Means, do.call(rbind, Stats)))
colnames(Stats)[5] <- "p"

# Hists 
# Re-arrange data for hists 
All_he <- list(Healthy_PDG_A_cert, Healthy_PDG_B_FH_cert, Healthy_PDG_B_SH_cert, Healthy_PDG_C_FH_cert, Healthy_PDG_C_SH_cert, Healthy_PDG_D_cert)

All_pat <- list(Pat_PDG_A_cert, Pat_PDG_B_FH_cert, Pat_PDG_B_SH_cert, Pat_PDG_C_FH_cert, Pat_PDG_C_SH_cert, Pat_PDG_D_cert)

All_he <- lapply(All_he, function(x) x*6+1)
All_pat <- lapply(All_pat, function(x) x*6+1)

All_he <- lapply(All_he, function(x){data.frame(table(x)/N_subj_healthy)})
All_pat <- lapply(All_pat, function(x){data.frame(table(x)/N_subj_pat)})

Hists_cert_ratings_PDG <- list()
for(i in seq(All_he)) {
x <- ggplot(NULL, aes(x=x, y=Freq))+
  stat_summary_bin(aes(fill = "Healthy"),
                   data=All_he[[i]],
                   fun.y="sum", geom = "bar", alpha=.5)+
  stat_summary_bin(aes(fill= "Patient"),
                   data=All_pat[[i]],
                   fun.y="sum", geom = "bar", alpha=.5)+
  theme(legend.position="bottom")+
  theme_grey()+
  ggtitle(sprintf("Seq %s", Seq_names[i]))+
  xlab("Final certainty ratings")+
  scale_y_continuous(limits=c(0, 1))
Hists_cert_ratings_PDG[[i]] <- x
}

# Set the default theme
theme_set(theme_grey())

Legend <-  g_legend(Hists_cert_ratings_PDG[[1]])

p1 <- Hists_cert_ratings_PDG[[1]]
p2 <- Hists_cert_ratings_PDG[[2]]
p3 <- Hists_cert_ratings_PDG[[3]]
p4 <- Hists_cert_ratings_PDG[[4]]
p5 <- Hists_cert_ratings_PDG[[5]]
p6 <- Hists_cert_ratings_PDG[[6]]

grid.arrange(p1+theme(legend.position="none"), p2+theme(legend.position="none"), p3+theme(legend.position="none"), p4+theme(legend.position="none"), p5+theme(legend.position="none"), p6+theme(legend.position="none"), top = "Proportion of final certainty ratings, PDG", Legend)

htmlTable(txtRound(Stats, 3), align = c("c", "|"), align.header=c("c", "|"), col.columns=c("none", Blue),
          caption = "Healthy vs patient final certainty scores, PDG")

# beads cert scores
Healthy_beads_A_cert <- apply(Healthy_beads[A_beads_ind], 1, max)
# Healthy_beads_B_cert <- apply(Healthy_beads[B_beads_ind], 1, min)
Healthy_beads_B_FH_cert <- apply(Healthy_beads[B_FH_beads_ind], 1, max)
Healthy_beads_B_SH_cert <- apply(Healthy_beads[B_SH_beads_ind], 1, min)
# Healthy_beads_C_cert <- apply(Healthy_beads[C_beads_ind], 1, max)
Healthy_beads_C_FH_cert <- apply(Healthy_beads[C_FH_beads_ind], 1, min)
Healthy_beads_C_SH_cert <- apply(Healthy_beads[C_SH_beads_ind], 1, max)
Healthy_beads_D_cert <- apply(Healthy_beads[D_beads_ind], 1, min)

Pat_beads_A_cert <- apply(Patient_beads[A_beads_ind], 1, max)
# Pat_beads_B_cert <- apply(Patient_beads[B_beads_ind], 1, min)
Pat_beads_B_FH_cert <- apply(Patient_beads[B_FH_beads_ind], 1, max)
Pat_beads_B_SH_cert <- apply(Patient_beads[B_SH_beads_ind], 1, min)
# Pat_beads_C_cert <- apply(Patient_beads[C_beads_ind], 1, max)
Pat_beads_C_FH_cert <- apply(Patient_beads[C_FH_beads_ind], 1, min)
Pat_beads_C_SH_cert <- apply(Patient_beads[C_SH_beads_ind], 1, max)
Pat_beads_D_cert <- apply(Patient_beads[D_beads_ind], 1, min)

# Means
Means <- c(mean(Healthy_beads_A_cert), mean(Pat_beads_A_cert), mean(Healthy_beads_B_FH_cert), mean(Pat_beads_B_FH_cert), mean(Healthy_beads_B_SH_cert), mean(Pat_beads_B_SH_cert), mean(Healthy_beads_C_FH_cert), mean(Pat_beads_C_FH_cert), mean(Healthy_beads_C_SH_cert), mean(Pat_beads_C_SH_cert), mean(Healthy_beads_D_cert), mean(Pat_beads_D_cert))
dim(Means) <- c(2, 6)
Means <- t(Means)
colnames(Means) <- c("Healthy mean", "Pat mean")

# Test beads diffs in cert scores
Test_cert_A <- t.test(Healthy_beads_A_cert, Pat_beads_A_cert)
Test_cert_B_FH <- t.test(Healthy_beads_B_FH_cert, Pat_beads_B_FH_cert)
Test_cert_B_SH <- t.test(Healthy_beads_B_SH_cert, Pat_beads_B_SH_cert)
Test_cert_C_FH <- t.test(Healthy_beads_C_FH_cert, Pat_beads_C_FH_cert)
Test_cert_C_SH <- t.test(Healthy_beads_C_SH_cert, Pat_beads_C_SH_cert)
Test_cert_D <- t.test(Healthy_beads_D_cert, Pat_beads_D_cert)

# Put together table
Stats <- list(Test_cert_A, Test_cert_B_FH, Test_cert_B_SH, Test_cert_C_FH, Test_cert_C_SH, Test_cert_D)
names(Stats) <- Seq_names
Stats <- lapply(Stats, function(x) {c(x$statistic, x$parameter, x$p.value)})
Stats <- data.frame(cbind(Means, do.call(rbind, Stats)))
colnames(Stats)[5] <- "p"

# Hists 
# Re-arrange data for hists 
All_he <- list(Healthy_beads_A_cert, Healthy_beads_B_FH_cert, Healthy_beads_B_SH_cert, Healthy_beads_C_FH_cert, Healthy_beads_C_SH_cert, Healthy_beads_D_cert)

All_pat <- list(Pat_beads_A_cert, Pat_beads_B_FH_cert, Pat_beads_B_SH_cert, Pat_beads_C_FH_cert, Pat_beads_C_SH_cert, Pat_beads_D_cert)

All_he <- lapply(All_he, function(x) x*6+1)
All_pat <- lapply(All_pat, function(x) x*6+1)

All_he <- lapply(All_he, function(x){data.frame(table(x)/N_subj_healthy)})
All_pat <- lapply(All_pat, function(x){data.frame(table(x)/N_subj_pat)})


Hists_cert_ratings_beads <- list()
for(i in seq(All_he)) {
x <- ggplot(NULL, aes(x=x, y=Freq))+
  stat_summary_bin(aes(fill = "Healthy"),
                   data=All_he[[i]],
                   fun.y="sum", geom = "bar", alpha=.5)+
  stat_summary_bin(aes(fill= "Patient"),
                   data=All_pat[[i]],
                   fun.y="sum", geom = "bar", alpha=.5)+
  theme(legend.position="bottom")+
  theme_grey()+
  ggtitle(sprintf("Seq %s", Seq_names[i]))+
  xlab("Final certainty ratings")+
  scale_y_continuous(limits=c(0, 1))
Hists_cert_ratings_beads[[i]] <- x
}

# Set the default theme
theme_set(theme_grey())

Legend <-  g_legend(Hists_cert_ratings_beads[[1]])

p1 <- Hists_cert_ratings_beads[[1]]
p2 <- Hists_cert_ratings_beads[[2]]
p3 <- Hists_cert_ratings_beads[[3]]
p4 <- Hists_cert_ratings_beads[[4]]
p5 <- Hists_cert_ratings_beads[[5]]
p6 <- Hists_cert_ratings_beads[[6]]

grid.arrange(p1+theme(legend.position="none"), p2+theme(legend.position="none"), p3+theme(legend.position="none"), p4+theme(legend.position="none"), p5+theme(legend.position="none"), p6+theme(legend.position="none"), top = "Proportion of final certainty ratings, beads", Legend)

htmlTable(txtRound(Stats, 3), align = c("c", "|"), align.header=c("c", "|"), col.columns=c("none", Blue),
          caption = "Healthy vs patient final certainty scores, beads")

```
**-------------------------------------------------------------------------------------------------**

#### 1b. First-half DTC using lower criteria for certainty - Likert scales 2 & 6 - in both tasks.

##### NB - if subjects took more than 5 trials to certainty, this was counted as '5', so there were **at least** 5 trials to certainty. 

```{r echo=F, warning=FALSE, message=FALSE}

# SETUP NO OF TRIALS TO 0.167/0.833 / 2/6

Two <- Values[2]
Six <- Values[(length(Values)-1)]

# Healthy PDG
Healthy_PDG_DTC_A <- apply(Healthy_PDG_A[,c(1:5)], 1, function(x) min(which(x==Six)))
Healthy_PDG_DTC_A <- ifelse(Healthy_PDG_DTC_A==Inf, 5, Healthy_PDG_DTC_A)
Healthy_PDG_DTC_B <- apply(Healthy_PDG_B[,c(1:5)], 1, function(x) min(which(x==Six)))
Healthy_PDG_DTC_B <- ifelse(Healthy_PDG_DTC_B==Inf, 5, Healthy_PDG_DTC_B)
Healthy_PDG_DTC_C <- apply(Healthy_PDG_C[,c(1:5)], 1, function(x) min(which(x==Two)))
Healthy_PDG_DTC_C <- ifelse(Healthy_PDG_DTC_C==Inf, 5, Healthy_PDG_DTC_C)
Healthy_PDG_DTC_D <- apply(Healthy_PDG_D[,c(1:5)], 1, function(x) min(which(x==Two)))
Healthy_PDG_DTC_D <- ifelse(Healthy_PDG_DTC_D==Inf, 5, Healthy_PDG_DTC_D)

DTC_healthy_PDG <- (sum(c(Healthy_PDG_DTC_A, Healthy_PDG_DTC_B, 
                          Healthy_PDG_DTC_C, Healthy_PDG_DTC_D)) / 4) / N_subj_healthy

# Patient PDG
Pat_PDG_DTC_A <- apply(Patient_PDG_A[,c(1:5)], 1, function(x) min(which(x==Six)))
Pat_PDG_DTC_A <- ifelse(Pat_PDG_DTC_A==Inf, 5, Pat_PDG_DTC_A)
Pat_PDG_DTC_B <- apply(Patient_PDG_B[,c(1:5)], 1, function(x) min(which(x==Six)))
Pat_PDG_DTC_B <- ifelse(Pat_PDG_DTC_B==Inf, 5, Pat_PDG_DTC_B)
Pat_PDG_DTC_C <- apply(Patient_PDG_C[,c(1:5)], 1, function(x) min(which(x==Two)))
Pat_PDG_DTC_C <- ifelse(Pat_PDG_DTC_C==Inf, 5, Pat_PDG_DTC_C)
Pat_PDG_DTC_D <- apply(Patient_PDG_D[,c(1:5)], 1, function(x) min(which(x==Two)))
Pat_PDG_DTC_D <- ifelse(Pat_PDG_DTC_D==Inf, 5, Pat_PDG_DTC_D)

DTC_pat_PDG <- (sum(c(Pat_PDG_DTC_A, Pat_PDG_DTC_B,
                      Pat_PDG_DTC_C, Pat_PDG_DTC_D)) / 4) / N_subj_pat

# Healthy beads
Healthy_beads_DTC_A <- apply(Healthy_beads_A[,c(1:5)], 1, function(x) min(which(x==Six)))
Healthy_beads_DTC_A <- ifelse(Healthy_beads_DTC_A==Inf, 5, Healthy_beads_DTC_A)
Healthy_beads_DTC_B <- apply(Healthy_beads_B[,c(1:5)], 1, function(x) min(which(x==Six)))
Healthy_beads_DTC_B <- ifelse(Healthy_beads_DTC_B==Inf, 5, Healthy_beads_DTC_B)
Healthy_beads_DTC_C <- apply(Healthy_beads_C[,c(1:5)], 1, function(x) min(which(x==Two)))
Healthy_beads_DTC_C <- ifelse(Healthy_beads_DTC_C==Inf, 5, Healthy_beads_DTC_C)
Healthy_beads_DTC_D <- apply(Healthy_beads_D[,c(1:5)], 1, function(x) min(which(x==Two)))
Healthy_beads_DTC_D <- ifelse(Healthy_beads_DTC_D==Inf, 5, Healthy_beads_DTC_D)

DTC_healthy_beads <- (sum(c(Healthy_beads_DTC_A, Healthy_beads_DTC_B,
                            Healthy_beads_DTC_C, Healthy_beads_DTC_D)) / 4) / N_subj_healthy

# Patient beads
Pat_beads_DTC_A <- apply(Patient_beads_A[,c(1:5)], 1, function(x) min(which(x==Six)))
Pat_beads_DTC_A <- ifelse(Pat_beads_DTC_A==Inf, 5, Pat_beads_DTC_A)
Pat_beads_DTC_B <- apply(Patient_beads_B[,c(1:5)], 1, function(x) min(which(x==Six)))
Pat_beads_DTC_B <- ifelse(Pat_beads_DTC_B==Inf, 5, Pat_beads_DTC_B)
Pat_beads_DTC_C <- apply(Patient_beads_C[,c(1:5)], 1, function(x) min(which(x==Two)))
Pat_beads_DTC_C <- ifelse(Pat_beads_DTC_C==Inf, 5, Pat_beads_DTC_C)
Pat_beads_DTC_D <- apply(Patient_beads_D[,c(1:5)], 1, function(x) min(which(x==Two)))
Pat_beads_DTC_D <- ifelse(Pat_beads_DTC_D==Inf, 5, Pat_beads_DTC_D)

DTC_pat_beads <- (sum(c(Pat_beads_DTC_A, Pat_beads_DTC_B,
                        Pat_beads_DTC_C, Pat_beads_DTC_D)) / 4) / N_subj_pat

DTC_lower <- signif(c(DTC_healthy_PDG, DTC_pat_PDG, DTC_healthy_beads, DTC_pat_beads), digits=3)

htmlTable(DTC_lower, cgroup=Tasks, n.cgroup= rep(2, N_tasks), header=rep(Groups, 2), 
          align = c("c", "|"), align.header=c("c", "|"), col.columns=c("none", Blue), 
          caption = "Av draws to either 2 or 6 (Likert) over first half, all seqs")

# Plot:
# PDG
DTC_healthy_PDG_all <- c(Healthy_PDG_DTC_A, Healthy_PDG_DTC_B, Healthy_PDG_DTC_C, Healthy_PDG_DTC_D)
DTC_pat_PDG_all <- c(Pat_PDG_DTC_A, Pat_PDG_DTC_B, Pat_PDG_DTC_C, Pat_PDG_DTC_D)

DTC_healthy_PDG_all_table <- data.frame((table(DTC_healthy_PDG_all)/N_subj_healthy)/4)
DTC_pat_PDG_all_table <- data.frame((table(DTC_pat_PDG_all)/N_subj_pat)/4)

colnames(DTC_healthy_PDG_all_table) <- c("Draw", "Freq")
colnames(DTC_pat_PDG_all_table) <- c("Draw", "Freq")

Number_DTC_PDG <- ggplot(NULL, aes(Draw, Freq))+
  theme_grey()+
  stat_summary_bin(aes(fill = "Healthy"),
                   data=DTC_healthy_PDG_all_table,
                   fun.y="sum", geom = "bar", alpha=.5)+
  stat_summary_bin(aes(fill= "Patient"), 
                   data=DTC_pat_PDG_all_table, 
                   fun.y="sum", geom = "bar", alpha=.5)+
  theme(legend.position="bottom")+
  ggtitle("Proportion of subjects reaching 2 or 6 by trial number, all seqs, PDG")+
  scale_y_continuous(limits=c(0, 1))
Number_DTC_PDG

# Beads 
DTC_healthy_beads_all <- c(Healthy_beads_DTC_A, Healthy_beads_DTC_B, Healthy_beads_DTC_C, Healthy_beads_DTC_D)
DTC_pat_beads_all <- c(Pat_beads_DTC_A, Pat_beads_DTC_B, Pat_beads_DTC_C, Pat_beads_DTC_D)

DTC_healthy_beads_all_table <- data.frame((table(DTC_healthy_beads_all)/N_subj_healthy)/4)
DTC_pat_beads_all_table <- data.frame((table(DTC_pat_beads_all)/N_subj_pat)/4)

colnames(DTC_healthy_beads_all_table) <- c("Draw", "Freq")
colnames(DTC_pat_beads_all_table) <- c("Draw", "Freq")

Number_DTC_beads <- ggplot(NULL, aes(Draw, Freq))+
  theme_grey()+
  stat_summary_bin(aes(fill = "Healthy"),
                   data=DTC_healthy_beads_all_table,
                   fun.y="sum", geom = "bar", alpha=.5)+
  stat_summary_bin(aes(fill= "Patient"), 
                   data=DTC_pat_beads_all_table, 
                   fun.y="sum", geom = "bar", alpha=.5)+
  theme(legend.position="bottom")+
  ggtitle("Proportion of subjects reaching 2 or 6 by trial number, all seqs, beads")+
  scale_y_continuous(limits=c(0, 1))
Number_DTC_beads


```


<!--##### How many subjects (as a proportion of total group numbers) make a DTC at which indeces?-->

```{r echo=F, warning=FALSE, message=FALSE}

# Get_how_many_DTC()

# # Plots of how many subj DTC
# DTC_PDG <- ggplot(NULL, aes(Draws, Proportion_subjects))+
#   theme_grey()+
#   stat_summary_bin(aes(fill = "Healthy"),
#                    data=How_many_DTC_healthy_PDG,
#                    fun.y="sum", geom = "bar", alpha=.5)+
#   stat_summary_bin(aes(fill= "Patient"), 
#                    data=How_many_DTC_pat_PDG, 
#                    fun.y="sum", geom = "bar", alpha=.5)+
#   theme(legend.position="bottom")+
#   ggtitle("PDG")+
#   scale_y_continuous(limits=c(0, 0.15))
#   
# 
# DTC_beads <- ggplot(NULL, aes(Draws, Proportion_subjects))+
#   stat_summary_bin(aes(fill = "Healthy"),
#                    data=How_many_DTC_healthy_beads,
#                    fun.y="sum", geom = "bar", alpha=.5)+
#   stat_summary_bin(aes(fill= "Patient"), 
#                    data=How_many_DTC_pat_beads, 
#                    fun.y="sum", geom = "bar", alpha=.5)+
#   ggtitle("Beads")+
#   scale_y_continuous(limits=c(0, 0.15))+
#   theme_grey()+
#   theme(legend.position="none")
# 
# Legend <- g_legend(DTC_PDG)
# grid.arrange(DTC_PDG+theme(legend.position="none"), DTC_beads, Legend, ncol=2, nrow=2, 
#              layout_matrix=rbind(c(1, 2), c(3, 3)), 
#              top="Proportion of subjects making DTC, averaged across all four beads tasks",
#              widths=c(2.7, 2.7), heights=c(2.5, 0.2))


```


**-------------------------------------------------------------------------------------------------**

#### 2. Second half DTC - How many trials until subjects reach maximum certainty after the change of jar/trustworthiness in Seq B and Seq C only.

```{r echo=F, warning=FALSE, message=FALSE}

# Get second half indeces of seqs B & C, PDG & beads
Index_PDG_B <- 16:20
Index_PDG_C <- 26:30

Index_beads_C <- 16:20
Index_beads_B <- 26:30

# PDG
Healthy_PDG_B <- Healthy_PDG[Index_PDG_B] # Blue 1st half (1), Red 2nd (0)
Healthy_PDG_C <- Healthy_PDG[Index_PDG_C] # Red 1st (0), Blue 2nd (1)

Patient_PDG_B <- Patient_PDG[Index_PDG_B]
Patient_PDG_C <- Patient_PDG[Index_PDG_C]

# Beads
Healthy_beads_B <- Healthy_beads[Index_beads_B]
Healthy_beads_C <- Healthy_beads[Index_beads_C]

Patient_beads_B <- Patient_beads[Index_beads_B]
Patient_beads_C <- Patient_beads[Index_beads_C]

# Count how many draws to certainty, 2nd half BC

# Healthy PDG BC
SH_H_DTC_B <- apply(Healthy_PDG_B, 1, function(x) min(which(x==1)))
SH_H_DTC_B <- ifelse(SH_H_DTC_B==Inf, 5, SH_H_DTC_B)
SH_H_DTC_C <- apply(Healthy_PDG_C[,c(1:5)], 1, function(x) min(which(x==1)))
SH_H_DTC_C <- ifelse(SH_H_DTC_C==Inf, 5, SH_H_DTC_C)

DTC_healthy_PDG_BC <- (sum(c(SH_H_DTC_B, SH_H_DTC_C)) / 2) / N_subj_healthy

# Patient PGD BC

SH_Pat_DTC_B <- apply(Patient_PDG_B, 1, function(x) min(which(x==1)))
SH_Pat_DTC_B <- ifelse(SH_Pat_DTC_B==Inf, 5, SH_Pat_DTC_B)
SH_Pat_DTC_C <- apply(Patient_PDG_C, 1, function(x) min(which(x==1)))
SH_Pat_DTC_C <- ifelse(SH_Pat_DTC_C==Inf, 5, SH_Pat_DTC_C)

DTC_patient_PDG_BC <- (sum(c(SH_Pat_DTC_B, SH_Pat_DTC_C)) / 2) / N_subj_pat

# Healthy beads BC
SH_H_B_DTC_B <- apply(Healthy_beads_B, 1, function(x) min(which(x==1)))
SH_H_B_DTC_B <- ifelse(SH_H_B_DTC_B==Inf, 5, SH_H_B_DTC_B)
SH_H_B_DTC_C <- apply(Healthy_beads_C, 1, function(x) min(which(x==1)))
SH_H_B_DTC_C <- ifelse(SH_H_B_DTC_C==Inf, 5, SH_H_B_DTC_C)

DTC_healthy_beads_BC <- (sum(c(SH_H_B_DTC_B, SH_H_B_DTC_C)) / 2) / N_subj_healthy

# Patient beads BC
SH_pat_B_DTC_B <- apply(Patient_beads_B, 1, function(x) min(which(x==1)))
SH_pat_B_DTC_B <- ifelse(SH_pat_B_DTC_B==Inf, 5, SH_pat_B_DTC_B)
SH_pat_B_DTC_C <- apply(Patient_beads_C, 1, function(x) min(which(x==1)))
SH_pat_B_DTC_C <- ifelse(SH_pat_B_DTC_C==Inf, 5, SH_pat_B_DTC_C)

DTC_patient_beads_BC <- (sum(c(SH_pat_B_DTC_B, SH_pat_B_DTC_C)) / 2) / N_subj_pat

DTC_BC <- signif(c(DTC_healthy_PDG_BC, 
                   DTC_patient_PDG_BC, 
                   DTC_healthy_beads_BC, 
                   DTC_patient_beads_BC), digits=3)

htmlTable(DTC_BC, cgroup=Tasks, n.cgroup= rep(2, N_tasks), header=rep(Groups, 2), 
          align = c("c", "|"), align.header=c("c", "|"), col.columns=c("none", Blue), 
          caption = "Average draws to certainty over second half of seqs B & C")

# Plot:
# PDG
SH_DTC_healthy_PDG_all <- c(SH_H_DTC_B, SH_H_DTC_C)
SH_DTC_pat_PDG_all <- c(SH_Pat_DTC_B, SH_Pat_DTC_C)

SH_DTC_healthy_PDG_all_table <- data.frame((table(SH_DTC_healthy_PDG_all)/N_subj_healthy)/2)
SH_DTC_pat_PDG_all_table <- data.frame((table(SH_DTC_pat_PDG_all)/N_subj_pat)/2)

colnames(SH_DTC_healthy_PDG_all_table) <- c("Draw", "Freq")
colnames(SH_DTC_pat_PDG_all_table) <- c("Draw", "Freq")

SH_Number_DTC_PDG <- ggplot(NULL, aes(Draw, Freq))+
  theme_grey()+
  stat_summary_bin(aes(fill = "Healthy"),
                   data=SH_DTC_healthy_PDG_all_table,
                   fun.y="sum", geom = "bar", alpha=.5)+
  stat_summary_bin(aes(fill= "Patient"), 
                   data=SH_DTC_pat_PDG_all_table, 
                   fun.y="sum", geom = "bar", alpha=.5)+
  theme(legend.position="bottom")+
  ggtitle("Proportion of subjects reaching DTC in second half of seqs B & C, PDG")+
  scale_y_continuous(limits=c(0, 1))
SH_Number_DTC_PDG

# Beads
SH_DTC_healthy_beads_all <- c(SH_H_B_DTC_B, SH_H_B_DTC_C)
SH_DTC_pat_beads_all <- c(SH_pat_B_DTC_B, SH_pat_B_DTC_C)

SH_DTC_healthy_beads_all_table <- data.frame((table(SH_DTC_healthy_beads_all)/N_subj_healthy)/2)
SH_DTC_pat_beads_all_table <- data.frame((table(SH_DTC_pat_beads_all)/N_subj_pat)/2)

colnames(SH_DTC_healthy_beads_all_table) <- c("Draw", "Freq")
colnames(SH_DTC_pat_beads_all_table) <- c("Draw", "Freq")

SH_Number_DTC_beads <- ggplot(NULL, aes(Draw, Freq))+
  theme_grey()+
  stat_summary_bin(aes(fill = "Healthy"),
                   data=SH_DTC_healthy_beads_all_table,
                   fun.y="sum", geom = "bar", alpha=.5)+
  stat_summary_bin(aes(fill= "Patient"), 
                   data=SH_DTC_pat_beads_all_table, 
                   fun.y="sum", geom = "bar", alpha=.5)+
  theme(legend.position="bottom")+
  ggtitle("Proportion of subjects reaching DTC in second half of seqs B & C, PDG")+
  scale_y_continuous(limits=c(0, 1))
SH_Number_DTC_beads


```

**-------------------------------------------------------------------------------------------------**

#### 3. The initial decision whether to cooperate/compete in the PDG in all four sequences.

```{r echo=F, warning=FALSE, message=FALSE}

# set WD
tryCatch({
  setwd("U:/Gilleen_data")
}, error=function(e) {
  setwd("~/Dropbox/Gilleen_Analysis/For Gary")
})

Healthy_PDG_act <- read.csv("Gilleen_healthy_PDG_action.csv", header=TRUE)
Pat_PDG_act <- read.csv("Gilleen_patient_PDG_action.csv", header=TRUE)

# Drop ID and save
Healthy_ID_PDG_action <- Healthy_PDG_act[,1]
Patient_ID_PDG_action <- Pat_PDG_act[,1]

Healthy_PDG_act <- Healthy_PDG_act[,-1]
Pat_PDG_act <- Pat_PDG_act[,-1]

# Get initial compete/cooperate actions
Indeces <- c(1, 11, 21, 31)
Healthy_actions <- Healthy_PDG_act[, Indeces]
Healthy_actions <- unname(unlist(Healthy_actions))

Pat_actions <- Pat_PDG_act[, Indeces]
Pat_actions <- unname(unlist(Pat_actions))

# Get proportions
Healthy_prop_compete <- sum(Healthy_actions==1) / N_subj_healthy / 4 # Compete
Healthy_prop_cooperate <- sum(Healthy_actions==2) / N_subj_healthy / 4 # Cooperate

Pat_prop_compete <- sum(Pat_actions==1) / N_subj_pat / 4
Pat_prop_cooperate <- sum(Pat_actions==2) / N_subj_pat / 4

# Standard errors
SE_prop <- function(p, n){
  sqrt((p*(1-p))/n)
}

SE_healthy_compete <-  SE_prop(Healthy_prop_compete, N_subj_healthy)
SE_healthy_cooperate <- SE_prop(Healthy_prop_cooperate, N_subj_healthy)
SE_pat_compete <- SE_prop(Pat_prop_compete, N_subj_pat)
SE_pat_cooperate <- SE_prop(Pat_prop_cooperate, N_subj_pat)

SE_action <- c(SE_healthy_compete, SE_healthy_cooperate, SE_pat_compete, SE_pat_cooperate)
# Limits <- aes()

# Put proportions into dataframe & htmlTable
Action_table <- signif(c(Healthy_prop_compete, Healthy_prop_cooperate, 
                         Pat_prop_compete, Pat_prop_cooperate), digits=3)

Action_table_total <- rbind(c(sum(Healthy_actions==1), sum(Healthy_actions==2), 
                        sum(Pat_actions==1), sum(Pat_actions==2)), Action_table)

htmlTable(Action_table_total, cgroup=Groups, n.cgroup= rep(2, N_tasks), header=rep(Action, 2), 
          align = c("c", "|"), align.header=c("c", "|"), col.columns=c("none", Blue), 
          rnames=c("Total", "Proportion"),
          caption = "Proportion of subjects' initial decisions in PDG, 
          across all four seqs")

Groups <- c(rep("Healthy", 2), rep("Patient", 2))

Group_action <- c("Healthy_compete", "Healthy_cooperate", "Patient_compete", "Patient_cooperate")

Action_df <- data.frame(Groups, Group_action, Action_table)

Initial_plot <- ggplot(Action_df, aes(x=Group_action, y=Action_table, fill=Groups))+
  geom_bar(stat="identity") +
  scale_fill_discrete(name="Group", 
                      breaks=c(1, 2), 
                      labels=c("Healthy", "Patient"))+
  xlab("Group & action")+ylab("Proportion of subjects")+
  geom_errorbar(aes(ymin=Action_table-SE_action, ymax=Action_table+SE_action), width=0.25)+
  theme_gray()
Initial_plot

# Stats
# Question: Do healthy differ from groups in the number of compete moves?

Group <- c(rep("Healthy",  N_subj_healthy*4), rep("Patient", N_subj_pat*4))

Test <- data.frame(Action=c(Healthy_actions, Pat_actions), Group)
           
Table <- xtabs(~ Group+Action, data=Test)
Prop_test <- prop.test(Table)

Test_table <- signif(c(Prop_test$statistic, Prop_test$parameter, Prop_test$p.value), digits=3)

htmlTable(Test_table, header=c("Chi-sq", "d.f.", "p"), 
          align = c("c", "|"), align.header=c("c", "|"), col.columns=c("none", Blue), 
          caption = txtMergeLines("Chi-sq test of proportions for initial action on PDG"))


```

**-------------------------------------------------------------------------------------------------**

#### 4. The average trust ratings on each trial the same in Seq A and Seq D ('mostly cooperate', 'mostly compete', respectively).

```{r echo=F, warning=FALSE, message=FALSE}

Index_A <- 1:10  # Mostly 1 - cooperate?
Index_D <- 31:40 # Mostly 0 - compete?

Healthy_PDG_A <- Healthy_PDG[Index_A]
Healthy_PDG_D <- Healthy_PDG[Index_D]

Pat_PDG_A <- Patient_PDG[Index_A]
Pat_PDG_D <- Patient_PDG[Index_D]

options(digits=3)

Test_A <- sapply(seq(Healthy_PDG_A), function(i) t.test(Healthy_PDG_A[,i], Pat_PDG_A[,i]))
Test_D <- sapply(seq(Healthy_PDG_D), function(i) t.test(Healthy_PDG_D[,i], Pat_PDG_D[,i]))

# Get vector of p-vals
P_vals <- c(signif(unlist(Test_A["p.value",]), digits=3), signif(unlist(Test_D["p.value",]), digits=3) )

Sig <- c(which(P_vals <= 0.05) )

# Plot Seqs A and D
Plot_PDG_AD <- function(){
  ggplot(Healthy_PDG_sum[c(Index_A, Index_D), ], aes(x=Sequence, y=Data, group=1)) +
    geom_errorbar(aes(ymin=Data-se, ymax=Data+se), width=.2)+
    geom_line(colour = "red", size = 1, alpha=.7)+
    geom_errorbar(data=Patient_PDG_sum[c(Index_A, Index_D), ],
                  aes(ymin=Data-se, ymax=Data+se), width=.2)+
    geom_line(data=Patient_PDG_sum[c(Index_A, Index_D), ], 
              aes(x=Sequence, y=Data), colour = "blue", size = 1, alpha=.7)+
    geom_point(data=data.frame(Seq_PDG[c(Index_A, Index_D)]),
               aes(x=1:length(Seq_PDG[c(Index_A, Index_D)]),
                   y=Seq_PDG[c(Index_A, Index_D)], colour=factor(Seq_PDG[c(Index_A, Index_D)])),
               size=5, show.legend = FALSE) +
    scale_x_discrete(labels = Seq_PDG[c(Index_A, Index_D)])+
    expand_limits(x = c(1, (length(Seq_PDG)/2)+3))+
    scale_y_continuous(breaks = seq(0,1,0.1), limits = c(-0.1, 1.1))+
    ylab("Trustworthiness rating")+
    geom_vline(xintercept = c(10.5), linetype = "longdash")+
    geom_hline(yintercept = Values, alpha=Alpha_line)+
    annotate("text", x = c(5, 15), y=0.1, label = c("A", "D"), fontface = "bold")+
    annotate("text", x = Sig, y = 0.8, label="*", fontface="bold", size=8)+
    annotate("text", x = (length(Seq_PDG)/2)/2, y=c(-0.1, 1.1), label=c("Compete", "Cooperate"))+
    annotate("text", x=(length(Seq_PDG)/2)+1, y=Values, label=as.character(1:7), size=3 )+
    annotate("text", x = (length(Seq_PDG)/2)+2, y=0.5, label="Original scale", angle=270)+
    ggtitle("Mean PDG data, healthy (red) & patient (blue); * = significant.\n0 = totally untrustworthy, 1 = totally trustworthy ")+
    theme_grey()
}
# x11()
Plot_PDG_AD()

# Create tables of t-tests
Test_A_table <- Test_A[c("statistic", "parameter", "p.value"),]
colnames(Test_A_table) <- paste("Draw", as.character(1:10))

htmlTable(txtRound(Test_A_table, 3), 
          align = c("c", "|"), align.header=c("c", "|"), col.columns=c("none", Blue),
          rnames=c("t", "df", "p"),
          caption = txtMergeLines("t-tests on healthy vs patient for each draw, seq A"))

Test_D_table <- Test_D[c("statistic", "parameter", "p.value"),]
colnames(Test_D_table) <- paste("Draw", as.character(1:10))

htmlTable(txtRound(Test_D_table, 3), 
          align = c("c", "|"), align.header=c("c", "|"), col.columns=c("none", Blue),
          rnames=c("t", "df", "p"),
          caption = txtMergeLines("t-tests on healthy vs patient for each draw, seq A"))

```





